\def\GraphicsFolder{chapters/superconducting-instability/pictures}
\chapter{Superconducting instability}\label{chap:mft-sc-instability}

This chapter is devoted to studying the superconducting phase of the system. The only symmetry we assume to break is the $\mathrm{U}^\mathrm{c}(1)$ charge symmetry, thus allowing for superconducting fluctuations. As is described thoroughly in Sec.~\ref{subsec:sc-fock-analytical}, the hopping amplitude is renormalized because of the non-local attraction. The symmetry structure of the pairing mechanism determines the contributing Cooper fluctuations: for $s$-wave and $d$-wave superconductivity, only the o.s. Cooper term contributes; for $p_\ell$-wave superconductivity, the s.s. term contributes as well. In the following sections, a derivation containing both Cooper terms is proposed.

\section{The SC phase and its symmetries}\label{sec:sc-phase-theory}

The starting point is, as done for the other phases, the discussion of the symmetries of the SC phase. We said in introduction we are studying the 
\[
	\mathrm{SU}(2) \times \mathrm{U}^\mathrm{c}(1) \times (\text{Point group})
	\quad\stackrel{\mathrm{SSB}}{\to}\quad
	\mathrm{SU}(2) \times (\text{Point group})
\]
symmetry breaking. Therefore the system density we assume to be uniform across all sites, similarly to the normal phase discussed in Chap.~\ref{chap:normal-phase}. \todo

Let us highlight now an important point regarding the Cooper class Wick's contractions performed on the general EHM of Eq.~\eqref{eq:extended-hubbard-model},
\[
	\hat H =
	\underbrace{
		-t \sum_{\langle ij \rangle} \sum_\sigma \hat c_{i\sigma}^\dagger \hat c_{j\sigma}
	}_{\hat H_t} \underbrace{
		+U \sum_i \hat c_{i\uparrow}^\dagger \hat c_{i\downarrow}^\dagger \hat c_{i\downarrow} \hat c_{i\uparrow}
		\vphantom{
			\sum_{\langle ij \rangle}
		}
	}_{\hat H_U}
	\underbrace{
		- V \sum_{\langle ij \rangle} \sum_{\sigma \sigma'} \hat c_{i\sigma}^\dagger \hat c_{j\sigma'}^\dagger \hat c_{j\sigma'} \hat c_{i\sigma}
	}_{\hat H_V}
\]
As is discussed in Sec.~\ref{sec:mft-discussion-non-local-source}, when applying Wick's theorem the resulting terms break the natural symmetries of the model. The superconducting symmetry we study breaks just the $\mathrm{U}^\mathrm{c}(1)$ charge conservation. Now, when dealing with superconducting Cooper pairing we need to account also for the spatial structure of the Cooper pair itself. Consider the generic Cooper fluctuation
\[
	\big\langle
	\hat c_{i\sigma}^\dagger \hat c_{j\sigma'}^\dagger
	\big\rangle
	\qq{with $i,j$ NN}
\]
From basic Quantum Mechanics we know the summation rules of the spin algebra $\mathfrak{su}(2)$,
\[
	\frac 1 2 \otimes \frac 1 2 = 0 \oplus 1
\]
The two pairing channels are, at this level, the singlet channel associated to total spin $0$ and the triplet channel associated to total spin $1$. If we impose a specific spatial symmetry on the hamiltonian the ground state wavefunction will follow naturally, and the pairing channel will be the one providing a total anti-symmetry to the full wavefunction. This gives a selection rule over the relevant pairings: if we work with space symmetric structures -- say, $s^*$-wave or $d$-wave -- the pairing will take place in singlet channel, allowing us to eliminate the triplet pairing. Working with antisymmetric structures, inversely, we can eliminate the singlet channel. This concept is summarized in Tab.~\ref{tab:sc-pairings-symmetry-structures}.

\begin{table}
	\centering
	\begin{tabular}{c c c}
		\textbf{Spatial structure} & \textbf{Pairing channel} & \textbf{RWCs in Cooper channel} \\
		\midrule
		Symmetric wave function & Singlet pairing & Just $\displaystyle \big\langle
		\hat c_{i\sigma}^\dagger \hat c_{j\overline{\sigma}}^\dagger
		\big\rangle$ \\
		Anti-symmetric wave function & Triplet pairing & Both $\displaystyle \big\langle
		\hat c_{i\sigma}^\dagger \hat c_{j\overline{\sigma}}^\dagger
		\big\rangle$ and $\displaystyle \big\langle
		\hat c_{i\sigma}^\dagger \hat c_{j\sigma}^\dagger
		\big\rangle$ \\
		\midrule
	\end{tabular}
	\caption{Relation of the Cooper pairing channel with the wavefunction spatial symmetry (intended as the inversion $(x,y) \to (-x,-y)$).}
	\label{tab:sc-pairings-symmetry-structures}
\end{table}

\subsection{Superconductivity in the HM}\label{subsec:sc-hm}

In Sec.~\ref{appsec:superconducting-phase}, we discuss in detail the (impossibility of a stable) $s$-wave SC phase in the conventional HM. This is an obvious result, since the two-body interaction thereby present $\hat H_U$ is local and repulsive. We nevertheless treat the model within the MFT framework, and here recall the main widely known results, and later use them as groundwork for the EHM extension. Similarly to Sec.~\ref{subsec:af-hm}, let us define the operators
\begin{align}
	\hat n_{\mathbf{k}\sigma} &\equiv \hat c_{\mathbf{k}\sigma}^\dagger \hat c_{\mathbf{k}\sigma} \label{eq:sc-ehm-n-def} \\
	\hat \phi_\mathbf{k} &\equiv \hat c_{\mathbf{k}\uparrow}^\dagger \hat c_{-\mathbf{k}\downarrow}^\dagger \label{eq:sc-ehm-phi-def}
\end{align}
whose EVs are relevant for the SC phase. Let:
\begin{align}
	u_{\mathbf{q}\sigma} &\equiv \langle
	\hat n_{\mathbf{q}\sigma}
	\rangle \label{eq:sc-uqsigma-def} \\
	w_{\mathbf{q}\sigma} &\equiv \langle
	\hat \phi_\mathbf{q}^\dagger
	\rangle \label{eq:sc-wqsigma-def}
\end{align}

The MFT hamiltonian is given explicitly for the HM in Eq.~\eqref{appeq:sc-hm-mft-h},
\begin{multline*}
	\hat H_t + \hat H_U \stackrel{\mathrm{MFT}}{\simeq} \sum_{\mathbf{k} \in \mathrm{BZ}} \sum_\sigma \epsilon_{\mathbf{k}\sigma}
	\left[
	\hat c_{\mathbf{k}\sigma}^\dagger \hat c_{\mathbf{k}\sigma}
	- \hat c_{\mathbf{k}+\bm{\pi}\sigma}^\dagger \hat c_{\mathbf{k}+\bm{\pi}\sigma}
	\right] \\
	- \sum_{\mathbf{q}\in\mathrm{BZ}} \left[
	\Delta^{(s)} \hat \phi_\mathbf{q} + 
	\Delta^{(s)*} \hat \phi_\mathbf{q}^\dagger
	\right] + nU \times \hat N - \left[
	E_{\mathrm{H}/U}^{(\mathrm{SC})} + E_{\mathrm{C}/U}^{(\mathrm{SC})}
	\right]
\end{multline*}
with $E_{\mathrm{H}/U}^{(\mathrm{SC})}$, $E_{\mathrm{C}/U}^{(\mathrm{SC})}$ the contraction energies arising from Hartree and Cooper channels, respectively in Eq.~\eqref{appeq:sc-hm-hartree-U-Ec} and \eqref{appeq:sc-hm-hartree-C-Ec}. In deriving this result we decomposed the interaction of the intermediate passage of Eq.~\eqref{appeq:sc-hm-U-int-2} and assumed the Cooper pair to have null total momentum. Moreover, we recognized in the passage of Eq.~\eqref{appeq:sc-hm-U-int-3} the presence of a $s$-wave harmonic transform of the function $w_\mathbf{q}$, and thus defined in Eq.~\eqref{appeq:sc-hm-ws-self-consistency},
\[
	w^{(s)} \equiv \frac{1}{L_x L_y} \sum_{\mathbf{q}\in\mathrm{BZ}} w_\mathbf{q}
	\qq{and}
	\Delta^{(s)} \equiv -U w^{(s)}
\]

Nambu-Bogoliubov representation of the MFT hamiltonian is given in Eq.~\eqref{sc-hm-bogoliubov-h} and equivalently in Eq.~\eqref{af-sc-spin-h},
\[
	\hat H_t + \hat H_U - \mu \hat N \simeq \sum_{\mathbf{k} \in \mathrm{BZ}} \sum_\sigma \hat \Phi_\mathbf{k}^\dagger h_\mathbf{k} \hat \Phi_\mathbf{k} - \left[
	E_{\mathrm{A}/t}^{(\mathrm{SC})} + E_{\mathrm{H}/U}^{(\mathrm{SC})} + E_{\mathrm{C}/U}^{(\mathrm{SC})}
	\right]
\]
being
\[
	h_\mathbf{k} \equiv \begin{bmatrix}
		\xi_\mathbf{k} & -\Delta_\mathbf{k} \\
		-\Delta_\mathbf{k}^* & - \xi_\mathbf{k}
	\end{bmatrix}
	\qq{and}
	\xi_\mathbf{k} \equiv \epsilon_\mathbf{k} - \tilde{\mu}
\]
and $\Delta_\mathbf{k} = \Delta^{(s)}$. Nambu spinors are, in this case,
\[
	\hat \Phi_\mathbf{k} \equiv \begin{bmatrix}
		\hat c_{\mathbf{k}\uparrow} \\
		\hat c_{-\mathbf{k}\downarrow}^\dagger
	\end{bmatrix}
\]

For the SC phase in the HM model, in general, we can admit for a complex gap function -- although being the gap a constant it can always be reduced to a purely real gap. Diagonalization by the angles defined in Eq.~\eqref{appeq:sc-hm-pseudofield} is performed via the composed rotation of Eq.~\eqref{appeq:sc-hm-diagonalizer},
\[
	W_\mathbf{k} = \begin{bmatrix}
		\cos \theta_\mathbf{k} e^{-i\zeta_\mathbf{k}} & - \sin \theta_\mathbf{k} e^{i\zeta_\mathbf{k}} \\
		\sin \theta_\mathbf{k} e^{-i\zeta_\mathbf{k}} & \cos \theta_\mathbf{k} e^{i\zeta_\mathbf{k}}
	\end{bmatrix}
\]
The Bogoliubov bands are $\pm E_\mathbf{k} = \sqrt{\xi_\mathbf{k}^2 + \abs{\Delta_\mathbf{k}}^2}$. The only crucial difference with the AF Bogoliubov bands it that here, apart from the absence of the spin index -- a degeneracy that is solved now by enlarging the computation to the entire BZ --, also the bare bands $\epsilon_\mathbf{k}$ are substituted by their shifted version $\xi_\mathbf{k}$. This difference is essential: it is this feature that makes the superconducting phase gapped in an insulating sense, which means, opening the gap at the position of $\tilde{\mu}$. Instead for the AF phase the gap was always opened at ``midband'', the MBZ contour where $\epsilon_\mathbf{k}=0$. As a final remark, as is proven trivially at the end of Sec.~\ref{appsubsec:sc-hm-impossible}, $s$-wave SC is impossible at MFT level on the pure HM. This was obvious, due to the necessity of an even small attractive interaction to form Cooper pairs. To conclude, in Tab.~\ref{tab:sc-pseudospin-map} we report the operator-pseudospin map for each direction.

\begin{table}
	\centering
	\begin{tabular}{c c c}
		\textbf{EV} & \textbf{Meaning} & \textbf{Equation} \\
		\midrule
		$\ev{\hat s_\mathbf{k}^x}$ & $\ev{
			\hat \phi_\mathbf{k}
			+ \hat \phi_\mathbf{k}^\dagger
		}$ & \eqref{appeq:sc-hm-sx} \\[0.7em]
		$i\ev{\hat s_\mathbf{k}^y}$ & $\ev{
			\hat \phi_{\mathbf{k}\sigma}
			- \hat \phi_\mathbf{k}^\dagger
		}$ & \eqref{appeq:sc-hm-sy} \\[0.7em]
		$\ev{\hat s_\mathbf{k}^z}$ & $\ev{
			\hat n_{\mathbf{k}\uparrow}
			+ \hat n_{\mathbf{k}\downarrow}
		}  - 1$ & \eqref{appeq:sc-hm-sz} \\
		\midrule
	\end{tabular}
	\caption{List of the various expectation values (EVs) of each pseudospin component, their meaning in terms of fermionic operators and the reference equations from the pure HM. The $z$ component refers also to Eq.~\eqref{appeq:sc-hm-n-z}.}
	\label{tab:sc-pseudospin-map}
\end{table}

\subsection{Extension to the EHM}\label{subsec:sc-ehm}

Add now the non-local interaction $\hat H_V$: translational invariance is preserved while charge conservation is broken, thus all three channels (Hartree, Fock and Cooper) contribute via RWCs to the MFT hamiltonian. As for the AF phase, we aim to derive a MFT solution for the SC phase which is an extension of the HM solution of Sec.~\ref{appsec:superconducting-phase}, with an effective redefinition of the various physical quantities and mathematical objects,
\[
	\xi_\mathbf{k} \to \tilde{\xi}_\mathbf{k}
	\qquad
	E_\mathbf{k} \to \tilde{E}_\mathbf{k}
	\qquad
	\Delta_\mathbf{k} \to \tilde{\Delta}_\mathbf{k}
	\qquad
	\mu \to \tilde{\mu}
\]
To be completely correct, the chemical potential was already renormalized in the HM derivation in Sec.~\ref{appsubsec:sc-hartree-channel}. It here acquires yet another renormalization. The band energies renormalization is simply
\[
	\tilde{E}_\mathbf{k} \equiv \sqrt{\tilde{\xi}_\mathbf{k}^2 + |\tilde{\Delta}_\mathbf{k}|^2}
\]
and as for the AF phase:
\begin{align}
	\langle \hat \Phi_\mathbf{k}^\dagger \tau^x \hat \Phi_\mathbf{k} \rangle &= -\sin \normalfont(2\tilde{\theta}_\mathbf{k}) \sin \normalfont(2\tilde{\zeta}_\mathbf{k}) \langle \hat \Gamma_\mathbf{k}^\dagger \tau^z \hat \Gamma_\mathbf{k} \rangle \label{eq:sc-x-expectation-non-local}\\
	\langle \hat \Phi_\mathbf{k}^\dagger \tau^y \hat \Phi_\mathbf{k} \rangle &= -\sin \normalfont(2\tilde{\theta}_\mathbf{k}) \cos \normalfont(2\tilde{\zeta}_\mathbf{k}) \langle \hat \Gamma_\mathbf{k}^\dagger \tau^z \hat \Gamma_\mathbf{k} \rangle \label{eq:sc-y-expectation-non-local}\\
	\langle \hat \Phi_\mathbf{k}^\dagger \tau^z \hat \Phi_\mathbf{k} \rangle &= \cos \normalfont(2\tilde{\theta}_\mathbf{k}) \langle \hat \Gamma_\mathbf{k}^\dagger \tau^z \hat \Gamma_\mathbf{k} \rangle \label{eq:sc-z-expectation-non-local}
\end{align}
These equations are identical to the ones for the pure HM, Eqns.~\eqref{appeq:sc-hm-sx}, \eqref{appeq:sc-hm-sy} and \eqref{appeq:sc-hm-sz}. In the tilted frame, we have the analogous of Eq.~\eqref{eq:af-rot-z-expectation} with the important exception that the chemical potential in the Fermi-Dirac factors is zero,
\begin{equation}\label{eq:sc-rot-z-expectation}
	\langle \hat \Gamma_\mathbf{k}^\dagger \tau^z \hat \Gamma_\mathbf{k} \rangle = \frac{1}{2} \left[
		f\left(
			\tilde{E}_\mathbf{k};\beta,0
		\right) - f\left(
			-\tilde{E}_\mathbf{k};\beta,0
		\right)
	\right]
\end{equation}
This is because all the chemical potential operatorial contributions were absorbed in the bare bands $\tilde{\xi}_\mathbf{k}$, thus the pseudospin state is thermally described by an effective null chemical potential.

The (renormalized) thermal factors as in Eq.~\eqref{appeq:sc-thermal-factors-def} are
\begin{equation}\label{eq:sc-ren-thermal-factors-def}
	\tilde{\mathrm{Th}}_\mathbf{k}^{(\pm)}[\beta,\tilde{\mu}] \equiv
	f\left(
		\tilde{E}_\mathbf{k};\beta,0
	\right) \pm f\left(
		-\tilde{E}_\mathbf{k};\beta,0
	\right)
\end{equation}
which simply reduce to
\[
\begin{aligned}
	\tilde{\mathrm{Th}}_\mathbf{k}^{(+)} &= 1 \\
	\tilde{\mathrm{Th}}_\mathbf{k}^{(-)} &= - \tanh(\frac{\beta \tilde{E}_\mathbf{k}}{2})
\end{aligned}
\]

For the angles it holds
\begin{equation}\label{eq:sc-bogoliubov-angle-relations}
	\sin \normalfont(2\tilde{\xi}_\mathbf{k}) = \frac{\Re\{\tilde{\Delta}_\mathbf{k}\}}{|\tilde{\Delta}_\mathbf{k}|}
	\quad
	\cos \normalfont(2\tilde{\xi}_\mathbf{k}) = \frac{\Im\{\tilde{\Delta}_\mathbf{k}\}}{|\tilde{\Delta}_\mathbf{k}|}
	\quad
	\sin \normalfont(2\tilde{\theta}_\mathbf{k}) = \frac{|\tilde{\Delta}_\mathbf{k}|}{\tilde{E}_\mathbf{k}}
	\quad
	\cos \normalfont(2\tilde{\theta}_\mathbf{k}) = \frac{\tilde{\xi}_\mathbf{k}}{\tilde{E}_\mathbf{k}}
\end{equation}
From Tabs.~\ref{tab:U-wick-terms-phases} and \ref{tab:V-wick-terms-phases}, we know all channel contribute. It is already known the effect of the Fock contractions, responsible as for the normal phase (Chap.~\ref{chap:normal-phase}) of the bare bands renormalization. Cooper terms are to be handled more carefully, since can contribute to superconductivity both in the s.s. and in the o.s. spin sectors.

\section{Non-local Hartree effects: chemical potential renormalization}\label{sec:sc-hartree-mu}

As always, let us start with a very brief section about the Hartree effects on the MFT decomposition of the hamiltonian. We will not delve in the detailed calculations of the Hartree channel MFT effects, already described in previous chapter as well as in Sec.~\ref{appsec:superconducting-phase}. The only effect here is the chemical potential renormalization.

\subsection{Hartree channel in the SC phase: analytical derivation}\label{subsec:sc-hartree-analytical}

The Hartree fluctuations are density-density couplings in the MFT hamiltonian. Knowing the deal with a uniform-density phase, we can re-use as it is the derivation of Sec.~\ref{subsec:normal-hartree-analytical}. Without repeating the calculations, the $\hat H_V$ is reduced in the Hartree channel to
\[
	\hat H_V \simeq -2nzV \times \hat N - E_{\mathrm{H}/V}^{(\mathrm{SC})} + 
	(\text{all the rest})
\]
This, together with the $\hat H_U$ Hartree channel decomposition
\[
	\hat H_U \simeq nU \times \hat N - E_{\mathrm{H}/U}^{(\mathrm{SC})}
\]
gives the chemical potential full renormalization, identical to Eq.~\eqref{eq:normal-mu-shift},
\begin{equation}\label{eq:sc-mu-shift}
	\tilde{\mu} \equiv \mu + n(2zV-U)
\end{equation}

\subsection{Hartree contraction energy}\label{subsec:sc-hartree-energy}

The contraction energy for the non-local sector was derived in Eq.~\eqref{eq:normal-hartree-V-contraction-energy},
\[
	E_{\mathrm{H}/V}^{(\mathrm{SC})} = - L_x L_y \times 2zn^2 V
\]
and together with the local counterpart of  Eq.~\eqref{eq:normal-hartree-U-contraction-energy}
\[
	E_{\mathrm{H}/U}^{(\mathrm{SC})} = L_x L_y \times n^2U
\]
Now we move to the more interesing Fock sector.

\section{Fock effects: bare bands renormalization}\label{sec:sc-fock}
\todo

\subsection{Fock channel in the SC phase: analytical derivation}\label{subsec:sc-fock-analytical}

When it comes to the Fock RWCs, being the SC phase density-uniform we can re-use almost the entirety of the derivation of Sec.~\ref{sec:normal-fock-bands-renormalization}. Setting as in Eq.~\eqref{eq:normal-uqsigma-def}
\begin{equation}
	u_{\mathbf{q}\sigma} \equiv \langle
	\hat c_{\mathbf{q}\sigma}^\dagger
	\hat c_{\mathbf{q}\sigma}
	\rangle
\end{equation}
Eq.~\eqref{eq:normal-V-fock-int5} stands perfectly valid, translated to the SC phase
\begin{multline}
	V \sum_{\ev{ij}} \sum_\sigma \left[
	\langle
	\hat c_{i\sigma}^\dagger \hat c_{j\sigma}
	\rangle \hat c_{j\sigma}^\dagger  \hat c_{i\sigma} + 
	\hat c_{i\sigma}^\dagger \hat c_{j\sigma}
	\langle 
	\hat c_{j\sigma}^\dagger  \hat c_{i\sigma} 
	\rangle - \langle
	\hat c_{i\sigma}^\dagger \hat c_{j\sigma}
	\rangle \langle 
	\hat c_{j\sigma}^\dagger  \hat c_{i\sigma} \rangle
	\right] \\
	\stackrel{\mathcal{F}}{=} \sum_{\gamma,\sigma} \left[
	\frac{1}{L_x L_y} \sum_\mathbf{q\in\mathrm{BZ}} \varphi_\mathbf{q}^{(\gamma)}
	u_{\mathbf{q}\sigma}
	\right] \times V
	\sum_{\mathbf{q}'\in\mathrm{BZ}}
	\varphi_{\mathbf{q}'}^{(\gamma)*}
	\hat c_{\mathbf{q}'\sigma}^\dagger
	\hat c_{\mathbf{q}'\sigma} - E_{\mathrm{F}/V}^{(\mathrm{SC})} \label{eq:sc-V-fock-int1}
\end{multline}
being
\begin{equation}\label{eq:sc-V-fock-double-counting}
	E_{\mathrm{F}/V}^{(\mathrm{SC})} \equiv \frac{V}{L_x L_y} \sum_{\mathbf{q}, \mathbf{q}'} \sum_\sigma \left[
	\cos \left(
	\delta q_x
	\right)	+ \cos \left(
	\delta q_y
	\right)	
	\right]	
	\langle
	\hat c_{\mathbf{q}\sigma}^\dagger 
	\hat c_{\mathbf{q}\sigma}
	\rangle \langle
	\hat c_{\mathbf{q}'\sigma}^\dagger  \hat c_{\mathbf{q}'\sigma} 
	\rangle
\end{equation}
To get to this point, we employed the assumption
\[
	\langle \hat c_{\mathbf{k}\sigma}^\dagger \hat c_{\mathbf{k}' \sigma'} \rangle = \delta_{\mathbf{k}=\mathbf{k}'} \delta_{\sigma=\sigma'} \langle \hat c_{\mathbf{k} \sigma}^\dagger \hat c_{\mathbf{k} \sigma} \rangle
\]
which essentially states translational invariance and spin degeneracy. This assumption is obviously well-verified by the BCS ground state of Eq.~\mref. Recognising the symmetry decomposition
\[
	u^{(\gamma)}_\sigma = \frac{1}{L_x L_y} \sum_{\mathbf{q}\in\mathrm{BZ}} \varphi_\mathbf{q}^{(\gamma)}
	\langle
		\hat c_{\mathbf{q}\sigma}^\dagger
		\hat c_{\mathbf{q}\sigma}
	\rangle
\]
due to inversion symmetry the conclusion is identical to Eqns.~\eqref{eq:normal-V-fock-int5} and \eqref{eq:normal-bands-renormalization} (considering spin degeneracy),
\[
	\tilde{\epsilon}_\mathbf{k} \equiv \epsilon_\mathbf{k} + u^{(s^*)} V (\cos q_x + \cos q_y) + u^{(d)} V (\cos q_x - \cos q_y)
\]

In order to estimate the $\gamma$-wave components renormalizing the bare bands, we need to compute separately in spin sectors the EVs of $u_{\mathbf{k}\sigma}$
\begin{align}
	u_{\mathbf{k}\uparrow} &= \langle \hat c_{\mathbf{k}\uparrow}^\dagger \hat c_{\mathbf{k}\uparrow} \rangle \\	
	&= \ev{
		\hat \Phi_\mathbf{k}^\dagger \frac{\Id + \tau^z}{2} \hat \Phi_\mathbf{k}
	} \nonumber \\
	&= \frac{1}{2} \left[
		\ev{
			\hat \Gamma_\mathbf{k}^\dagger \hat \Gamma_\mathbf{k}
		} + \ev{\hat s_\mathbf{k}^z}
	\right] \nonumber \\
	&= \frac{1}{2} \left[
		\tilde{\mathrm{Th}}_\mathbf{k}^{(+)} [\beta] + 
		\cos 2 \tilde{\theta}_\mathbf{k} \tilde{\mathrm{Th}}_\mathbf{k}^{(-)} [\beta]
	\right] \nonumber \\
	&= \frac{1+\cos 2 \tilde{\theta}_\mathbf{k}}{2} f\left( \tilde{E}_\mathbf{k}; \beta,0 \right) + \frac{1-\cos 2 \tilde{\theta}_\mathbf{k}}{2} f\left( -\tilde{E}_\mathbf{k}; \beta,0 \right) \nonumber \\
	&= \cos^2 \tilde{\theta}_\mathbf{k} f\left( \tilde{E}_\mathbf{k}; \beta,0 \right) + \sin^2 \tilde{\theta}_\mathbf{k} f\left( -\tilde{E}_\mathbf{k}; \beta,0 \right) \nonumber \\
	&= \sin^2 \tilde{\theta}_\mathbf{k} \tanh(\frac{\beta \tilde{E}_\mathbf{k}}{2}) + f\left( \tilde{E}_\mathbf{k}; \beta,0 \right) \label{eq:sc-ehm-uUp-EV}
\end{align}
having we used the simple relation
\[
\begin{aligned}
	\frac{1}{e^{-x}+1} - \frac{1}{e^x+1} &= \frac{e^x -1}{e^x +1} \\
	&= \tanh(\frac{x}{2})
\end{aligned}
\]
For the spin $\downarrow$ EV,
\begin{align}
	u_{-\mathbf{k}\downarrow} &= \langle \hat c_{-\mathbf{k}\downarrow}^\dagger \hat c_{-\mathbf{k}\downarrow} \rangle \nonumber \\	
	&= 1 - \langle \hat c_{-\mathbf{k}\downarrow} \hat c_{-\mathbf{k}\downarrow}^\dagger \rangle \nonumber \\
	&= 1 - \ev{
		\hat \Phi_\mathbf{k}^\dagger \frac{\Id - \tau^z}{2} \hat \Phi_\mathbf{k}
	} \nonumber \\
	&= 1 - \frac{1}{2} \left[
	\ev{
		\hat \Gamma_\mathbf{k}^\dagger \hat \Gamma_\mathbf{k}
	} - \ev{\hat s_\mathbf{k}^z}
	\right] \nonumber \\
	&= 1 - \frac{1}{2} \left[
		\tilde{\mathrm{Th}}_\mathbf{k}^{(+)} [\beta] - 
		\cos 2 \tilde{\theta}_\mathbf{k} \tilde{\mathrm{Th}}_\mathbf{k}^{(-)} [\beta]
	\right] \nonumber \\
	&= 1 - \frac{1-\cos 2 \tilde{\theta}_\mathbf{k}}{2} f\left( \tilde{E}_\mathbf{k}; \beta,0 \right) - \frac{1+\cos 2 \tilde{\theta}_\mathbf{k}}{2} f\left( -\tilde{E}_\mathbf{k}; \beta,0 \right) \nonumber \\
	&= 1-\sin^2 \tilde{\theta}_\mathbf{k} f\left( \tilde{E}_\mathbf{k}; \beta,0 \right) - \cos^2 \tilde{\theta}_\mathbf{k} f\left( -\tilde{E}_\mathbf{k}; \beta,0 \right) \nonumber \\
	&= 1-\sin^2 \tilde{\theta}_\mathbf{k} \tanh(\frac{\beta \tilde{E}_\mathbf{k}}{2}) - f\left( -\tilde{E}_\mathbf{k}; \beta,0 \right) \nonumber \\
	&= -\sin^2 \tilde{\theta}_\mathbf{k} \tanh(\frac{\beta \tilde{E}_\mathbf{k}}{2}) + f\left( \tilde{E}_\mathbf{k}; \beta,0 \right) \label{eq:sc-ehm-uDown-EV}
\end{align}
These results will be used to extract self-consistency equations for each HFP. Note that
\[
	\lim_{\abs{\Delta_\mathbf{k}} \to 0} u_{\mathbf{k}\sigma} = f(\tilde{\xi}_\mathbf{k};\beta,0)
\]
Correctly, the null-gap limit reduces to a perfectly degenerate Fermi gas.

\subsection{Fock contraction energy}\label{subsec:sc-fock-energy}

In terms of the energy shift due to Wick's contraction, Eq.~\eqref{eq:normal-fock-V-contraction-energy} holds identically
\[
	E_{\mathrm{F}/V}^{(\mathrm{SC})} = L_x L_y \times \frac{V}{2} \sum_\sigma \left[
		\big|
			u^{(s^*)}
		\big|^2 + \big|
			u^{(d)}
		\big|^2
	\right]
\]
with the only obvious difference that the $u^{(\gamma)}$ are computed on the SC ground state by the means of Eqns.~\eqref{eq:sc-ehm-uUp-EV}, \eqref{eq:sc-ehm-uDown-EV}.

\section{Cooper channel in the o.s. and s.s. sectors}

Let us get back to the Fourier transform of Eq.~\eqref{eq:reciprocal-space-non-local-interaction-explicit}
\[
	\hat H_V \Feq - \frac{V}{L_x L_y} 	\sum_{\sigma\sigma'}
	\sum_{\mathbf{K}, \mathbf{k}, \mathbf{k}'} \left[
		\cos \left(
			\delta k_x
		\right)	+ \cos \left(
			\delta k_y
		\right)	
	\right]	\hat c_{\mathbf{K}+\mathbf{k} \sigma}^\dagger \hat c_{\mathbf{K}-\mathbf{k} \sigma'}^\dagger \hat c_{\mathbf{K}-\mathbf{k}' \sigma'} \hat c_{\mathbf{K}+\mathbf{k}'\sigma}
\]
which decomposes in s.s. and o.s. channels as:
\begin{multline*}
	\hat H_V \Feq 
	\overbrace{
		- \frac{V}{L_x L_y} \sum_{\sigma}
		\sum_{\mathbf{K}, \mathbf{k}, \mathbf{k}'} \left[
			\cos \left(
				\delta k_x
			\right)	+ \cos \left(
				\delta k_y
			\right)	
		\right]	\hat c_{\mathbf{K}+\mathbf{k} \sigma}^\dagger \hat c_{\mathbf{K}-\mathbf{k}\sigma}^\dagger \hat c_{\mathbf{K}-\mathbf{k}'\sigma} \hat c_{\mathbf{K}+\mathbf{k}'\sigma}
	}^{\mathrm{s.s.}} \\
	\underbrace{
		- \frac{V}{L_x L_y} \sum_{\sigma}
		\sum_{\mathbf{K}, \mathbf{k}, \mathbf{k}'} \left[
			\cos \left(
				\delta k_x
			\right)	+ \cos \left(
				\delta k_y
			\right)	
		\right]	\hat c_{\mathbf{K}+\mathbf{k} \sigma}^\dagger \hat c_{\mathbf{K}-\mathbf{k}\overline{\sigma}}^\dagger \hat c_{\mathbf{K}-\mathbf{k}'\overline{\sigma}} \hat c_{\mathbf{K}+\mathbf{k}'\sigma}
	}_{\mathrm{o.s.}}
\end{multline*}
Following Tab.~\ref{tab:sc-pairings-symmetry-structures}, in the singlet pairing channel only the o.s. sector produces RWCs. The latter is made up of two identical terms: this is because it holds
\[
	\hat c_{\mathbf{K}+\mathbf{k} \sigma}^\dagger \hat c_{\mathbf{K}-\mathbf{k}\overline{\sigma}}^\dagger \hat c_{\mathbf{K}-\mathbf{k}'\overline{\sigma}} \hat c_{\mathbf{K}+\mathbf{k}'\sigma} = \hat c_{\mathbf{K}-\mathbf{k}\overline{\sigma}}^\dagger \hat c_{\mathbf{K}+\mathbf{k} \sigma}^\dagger \hat c_{\mathbf{K}+\mathbf{k}'\sigma} \hat c_{\mathbf{K}-\mathbf{k}'\overline{\sigma}} 
\]
due to fermionic anti-commutation rules, and since the composite transform
\[
	\mathbf{k} \to -\mathbf{k}
	\qquad
	\mathbf{k}' \to -\mathbf{k}'	
\]
leaves the form factor $\cos \left( \delta k_x \right)	+ \cos \left( \delta k_y \right)$ invariant, we reduce the spin sum to two times the $\sigma=\uparrow$ part,
\begin{equation}\label{eq:sc-HV-os}
	\hat H_V^{(\mathrm{o.s.})} = - \frac{2V}{L_x L_y}
	\sum_{\mathbf{K}, \mathbf{k}, \mathbf{k}'} \left[
		\cos \left(
			\delta k_x
		\right)	+ \cos \left(
			\delta k_y
		\right)	
	\right]	\hat c_{\mathbf{K}+\mathbf{k} \uparrow}^\dagger \hat c_{\mathbf{K}-\mathbf{k}\downarrow}^\dagger \hat c_{\mathbf{K}-\mathbf{k}'\downarrow} \hat c_{\mathbf{K}+\mathbf{k}'\uparrow}
\end{equation}
\todo

\section{Cooper effects in the singlet channel: gap renormalization}\label{sec:sc-cooper}

\todo

\subsection{Cooper-singlet channel in the SC phase: analytical derivation}

This section deals with Cooper fluctuations induced by the o.s. part of the non-local hamiltonian --referring to the notation of Eq.~\eqref{eq:ehm-non-local-ss-os-terms}-- somewhat the simplest form of Cooper pairing. This sector contributes both to singlet pairing and triplet pairing. Considering Cooper fluctuations in the singlet channel, we need to break $\mathrm{U}^\mathrm{c}(1)$ symmetry imposing space inversion symmetry, while for the triplet anti-symmetry is required. Set as in Eq.~\eqref{eq:sc-wqsigma-def} the EV
\[
	w_\mathbf{q} = \langle
		\hat \phi_\mathbf{q}^\dagger
	\rangle
\]
Let us now break down the MFT discussion for the local and non-local interactions.

\paragraph{Local repulsion.}

The detailed treatment of $\hat H_U$ is discussed in Sec.~\ref{appsubsec:sc-cooper-channel}, in the context of conventional HM. We here just sketch the most important results. By contracting in the Cooper channel the Fourier transform of $\hat H_U$ of Eq.~\eqref{eq:reciprocal-space-local-interaction-explicit},
\[
	\hat H_U \Feq \frac{U}{L_x L_y}
	\sum_{\mathbf{K}, \mathbf{k}, \mathbf{k}'} \hat c_{\mathbf{K}+\mathbf{k} \uparrow}^\dagger \hat c_{\mathbf{K}-\mathbf{k} \downarrow}^\dagger \hat c_{\mathbf{K}-\mathbf{k}' \downarrow} \hat c_{\mathbf{K}+\mathbf{k}' \uparrow}
\]
in the hypothesis that preserving space translations invariance the net momentum of the Cooper pair is null, as in Eq.~\eqref{appeq:sc-hm-U-int-3} the local part of the hamiltonian is reduced to
\begin{equation}\label{eq:sc-U-cooper-int1}
	\hat H_U \simeq \text{(Hartree channel)} + \frac{U}{L_x L_y} \sum_{\mathbf{q},\mathbf{q}'} \left[
		w_\mathbf{q} \hat \phi_{\mathbf{q}'} + w_{\mathbf{q}'}^* \hat \phi_\mathbf{q}^\dagger
	\right] - E_{\mathrm{C}/U}^{(\mathrm{SC})}
\end{equation}
being $E_{\mathrm{C}/U}^{(\mathrm{SC})}$ the Cooper contraction given in Eq.~\eqref{appeq:sc-hm-hartree-C-Ec}. The Hartree channel is discussed in Sec.~\ref{appsubsec:sc-hartree-channel}. Let now:
\[
	w^{(s)} \equiv \frac{1}{L_x L_y} \sum_{\mathbf{q}\in\mathrm{BZ}} w_\mathbf{q}
\]
which reduces Eq.~\eqref{eq:sc-U-cooper-int1} to
\begin{equation}\label{eq:sc-U-cooper-int2}
	\hat H_U \simeq \text{(Hartree channel)} + U \sum_{\mathbf{q}\in\mathrm{BZ}} \left[
		w^{(s)} \hat \phi_\mathbf{q} + w^{(s)*} \hat \phi_\mathbf{q}^\dagger
	\right] - E_{\mathrm{C}/U}^{(\mathrm{SC})}
\end{equation}
As in Eq.~\eqref{appeq:sc-hm-U-int-4}, this will produce the $s$-wave part of the gap function.

%{\color{tabred}
%Consider first the local part,
%\[
%	\hat H_U = U \sum_{i \in \mathcal{S}} \hat n_{i\uparrow} \hat n_{i\downarrow} \simeq U \sum_{i \in \mathcal{S}} \left[
%		\big\langle
%			\hat c_{i\uparrow}^\dagger \hat c_{i\downarrow}^\dagger
%		\big\rangle
%		\hat c_{i\downarrow} \hat c_{i\uparrow} + \hat c_{i\uparrow}^\dagger \hat c_{i\downarrow}^\dagger \big\langle
%			\hat c_{i\downarrow} \hat c_{i\uparrow}
%		\big\rangle
%	\right]
%\]
%and use the result of Eq.~\eqref{eq:reciprocal-space-local-interaction-explicit},
%\[
%	\hat H_U \simeq \frac{U}{L_x L_y}
%	\sum_{\mathbf{K}, \mathbf{k}, \mathbf{k}'}
%	\left[
%		\big\langle
%			\hat c_{\mathbf{K}+\mathbf{k} \uparrow}^\dagger \hat c_{\mathbf{K}-\mathbf{k} \downarrow}^\dagger
%		\big\rangle
%		\hat c_{\mathbf{K}-\mathbf{k}' \downarrow} \hat c_{\mathbf{K}+\mathbf{k}' \uparrow} +
%		\hat c_{\mathbf{K}+\mathbf{k} \uparrow}^\dagger \hat c_{\mathbf{K}-\mathbf{k} \downarrow}^\dagger
%		\big\langle
%			\hat c_{\mathbf{K}-\mathbf{k}' \downarrow} \hat c_{\mathbf{K}+\mathbf{k}' \uparrow}
%		\big\rangle
%	\right]
%\]
%We are not breaking translational invariance, thus only Cooper fluctuations with net zero total momentum are allowed. This means only $\mathbf{K}=\mathbf{0}$ contributes. Define the pairing operators
%\[
%	\hat \phi_\mathbf{k} \equiv \hat c_{-\mathbf{k}\downarrow} \hat c_{\mathbf{k} \uparrow}
%	\qquad
%	\hat \phi_\mathbf{k}^\dagger \equiv \hat c_{\mathbf{k} \uparrow}^\dagger \hat c_{-\mathbf{k}\downarrow}^\dagger
%\]
%Then the non local repulsion reduces to the ordinary BCS-like interaction,
%\begin{equation}\label{eq:sc-ugap-mft}
%	\hat H_U \simeq \sum_\mathbf{k} \left[
%		\mathcal{U}_\mathbf{k} \hat \phi_\mathbf{k} + \mathcal{U}_\mathbf{k}^* \hat \phi_\mathbf{k}^\dagger
%	\right]
%\end{equation}
%where the MFT parameter $\mathcal{U}_\mathbf{k}$ must satisfy the self-consistency equation
%\begin{equation}\label{eq:sc-ugap-self-consistency}
%	\mathcal{U}_\mathbf{k} \equiv \frac{U}{L_x L_y} \sum_\mathbf{k} \big\langle 
%		\hat \phi_\mathbf{k}^\dagger
%	\big\rangle
%\end{equation}
%Note that $\mathcal{U}_\mathbf{k}$ is actually momentum independent. This is due to the fact that the repulsion is completely localized.}

\paragraph{Non-local attraction.}

Consider Eq.~\eqref{eq:sc-HV-os}, and perform Wick contractions, giving
%The non-local attraction in the opposite-spin sector of $\hat H_V$ is given by
%\[
%	\hat H_V^{(\mathrm{o.s.})} = -V \sum_{\ev{ij}} \sum_\sigma \hat n_{i\sigma} \hat n_{j\overline{\sigma}}
%\]
%which, using Eq.~\eqref{eq:ehm-mft-nonlocal-opposite-spin} and performing Wick's contractions, reduces to:
%\[
%\begin{aligned}
%	\hat H_V^{(\mathrm{o.s.})} &= -V \sum_{i \in \mathcal{S}} \sum_{\ell = x,y} \sum_{\delta = \pm \delta_\ell}
%	\hat n_{i\uparrow} \hat n_{i+\delta \downarrow} \\
%	&\simeq - V \sum_{i \in \mathcal{S}} \sum_{\ell = x,y} \sum_{\delta = \pm \delta_\ell} \left[
%		\langle 
%			\hat c_{i\uparrow}^\dagger \hat c_{i + \delta \downarrow}^\dagger
%		\rangle
%		\hat c_{i + \delta \downarrow} \hat c_{i\uparrow} 
%		+
%		\hat c_{i\uparrow}^\dagger \hat c_{i + \delta \downarrow}^\dagger
%		\langle
%			\hat c_{i + \delta \downarrow} \hat c_{i\uparrow} 
%		\rangle
%	\right]
%\end{aligned}
%\]
%Using Eq.~\eqref{eq:reciprocal-space-non-local-interaction-explicit} we can move to reciprocal space,
\begin{multline*}
	\hat H_V^{(\mathrm{o.s.})} \simeq -\frac{2V}{L_x L_y}
	\sum_{\mathbf{K}, \mathbf{k}, \mathbf{k}'} \left[
		\cos \left(
			\delta k_x
		\right)	+ \cos \left(
			\delta k_y
		\right)	
	\right]
	\times \Big[ 
		\big\langle
			\hat c_{\mathbf{K}+\mathbf{k} \uparrow}^\dagger \hat c_{\mathbf{K}-\mathbf{k} \downarrow}^\dagger
		\big\rangle 
		\hat c_{\mathbf{K}-\mathbf{k}' \downarrow} \hat c_{\mathbf{K}+\mathbf{k}'\uparrow} \\
		+
		\hat c_{\mathbf{K}+\mathbf{k} \uparrow}^\dagger \hat c_{\mathbf{K}-\mathbf{k} \downarrow}^\dagger
		\big\langle 
			\hat c_{\mathbf{K}-\mathbf{k}' \downarrow} \hat c_{\mathbf{K}+\mathbf{k}'\uparrow}
		\big\rangle
		-
		\big\langle
			\hat c_{\mathbf{K}+\mathbf{k} \uparrow}^\dagger \hat c_{\mathbf{K}-\mathbf{k} \downarrow}^\dagger
		\big\rangle
		\big\langle 
			\hat c_{\mathbf{K}-\mathbf{k}' \downarrow} \hat c_{\mathbf{K}+\mathbf{k}'\uparrow}
		\big\rangle
	\Big] + (\text{all the rest})
\end{multline*}
Identical considerations as above hold, and just the $\mathbf{K}=\mathbf{0}$ term contributes. We have finally
\begin{equation}\label{eq:sc-V-os-cooper-int1}
	\hat H_V^{(\mathrm{o.s.})} \simeq - \frac{2V}{L_x L_y} \sum_{\mathbf{q}, \mathbf{q}'} \left[
		\cos \left(
			\delta q_x
		\right)	+ \cos \left(
			\delta q_y
		\right)	
	\right]
	\left[
		w_\mathbf{q} \hat \phi_{\mathbf{q}'} + w_\mathbf{q}^* \hat \phi_{\mathbf{q}'}^\dagger
	\right]	- E_{\mathrm{C}/V/\mathrm{o.s.}}^{(\mathrm{SC})} + (\text{all the rest})
\end{equation}
where the contraction energy is
\begin{equation}\label{eq:sc-Vos-cooper-double-counting}
	E_{\mathrm{C}/V/\mathrm{o.s.}}^{(\mathrm{SC})} \equiv - \frac{2V}{L_x L_y} \sum_{\mathbf{q}, \mathbf{q}'} \left[
		\cos \left(
			\delta q_x
		\right)	+ \cos \left(
			\delta q_y
		\right)	
	\right] w_\mathbf{q} w_{\mathbf{q}'}^*
\end{equation}

Making use of the decomposition of Eq.~\eqref{eq:coscos-symmetries-decomposition}, Eq.~\eqref{eq:sc-V-os-cooper-int1} becomes
\[
\begin{aligned}
	\hat H_V^{(\mathrm{o.s.})} &\simeq -V
	\sum_\gamma \left[
		\frac{1}{L_x L_y} \sum_\mathbf{q} \varphi_\mathbf{q}^{(\gamma)} w_\mathbf{q}
	\right] \times \sum_{\mathbf{q}'} \varphi_{\mathbf{q}'}^{(\gamma)*} \hat \phi_{\mathbf{q}'} + \hc - E_{\mathrm{C}/V/\mathrm{o.s.}}^{(\mathrm{SC})} + (\text{all the rest}) \\
	&= -V \sum_\gamma \sum_{\mathbf{q}\in\mathrm{BZ}}
	w^{(\gamma)} \varphi_\mathbf{q}^{(\gamma)*} \hat \phi_\mathbf{q} + \hc - E_{\mathrm{C}/V/\mathrm{o.s.}}^{(\mathrm{SC})} + (\text{all the rest})
\end{aligned}
\]
extending the symmetry sum to $\gamma \in \lbrace s^*, p_x, p_y, d_{x^2-y^2} \rbrace$. As always, we used harmonics decomposition. The following chain, similar to Eq.~\eqref{appeq:sc-hm-ws-self-consistency-2}, holds:
\begin{align}
	w^{(\gamma)} &\equiv \frac{1}{L_x L_y} \sum_{\mathbf{k}\in\mathrm{BZ}} \varphi_\mathbf{k}^{(\gamma)} w_\mathbf{k} \nonumber \\
	&= \frac{1}{L_x L_y} \sum_{\mathbf{k}\in\mathrm{BZ}} \varphi_\mathbf{k}^{(\gamma)} \big\langle
		\hat \phi_\mathbf{k}^\dagger
	\big\rangle \nonumber \\
	&= \frac{1}{L_x L_y} \sum_{\mathbf{k}\in\mathrm{BZ}} \varphi_\mathbf{k}^{(\gamma)}  \big\langle
		\hat \Phi_\mathbf{k}^\dagger \tau^+ \hat \Phi_\mathbf{k}
	\big\rangle \nonumber \\
	&= \frac{1}{L_x L_y} \sum_{\mathbf{k}\in\mathrm{BZ}} \varphi_\mathbf{k}^{(\gamma)}  \left[
		\ev{\hat s_\mathbf{k}^x} + i \ev{\hat s_\mathbf{k}^y}
	\right] \nonumber \\
	&= - \frac{1}{L_x L_y} \sum_{\mathbf{k}\in\mathrm{BZ}} \varphi_\mathbf{k}^{(\gamma)} \frac{\tilde{\Delta}_\mathbf{k}}{\tilde{E}_\mathbf{k}} \tilde{\mathrm{Th}}_\mathbf{k}^{(-)}[\beta] \label{sc-hm-wgamma-self-consistency}
\end{align}
where $\tau^+ \equiv \tau^x + i \tau^y$. We used Eqns.~\eqref{eq:sc-x-expectation-non-local}, \eqref{eq:sc-y-expectation-non-local} and \eqref{eq:sc-rot-z-expectation} as well as the thermal factor defined in Eq.~\eqref{eq:sc-ren-thermal-factors-def}. The derivation above holds for all symmetries, including the $s$ one as testifies Eq.~\eqref{appeq:sc-hm-ws-self-consistency-2}. Explicitly, five self-consitency equations are then derived,
\begin{align}
	w^{(s^*)} &= \frac{1}{2L_x L_y} \sum_{\mathbf{k}\in\mathrm{MBZ}} (\cos k_x + \cos k_y)
	\frac{\Im\lbrace\tilde{\Delta}_\mathbf{k}\rbrace}{\tilde{E}_\mathbf{k}} \tanh(\frac{\beta\tilde{E}_\mathbf{k}}{2})
	\label{eq:sc-wS-self-consistency}\\
	w^{(d)} &= \frac{1}{2L_x L_y} \sum_{\mathbf{k}\in\mathrm{MBZ}} (\cos k_x - \cos k_y)
	\frac{\Im\lbrace\tilde{\Delta}_\mathbf{k}\rbrace}{\tilde{E}_\mathbf{k}} \tanh(\frac{\beta\tilde{E}_\mathbf{k}}{2})
	\label{eq:sc-wd-self-consistency}\\
	-iw^{(p_x)} &= \frac{1}{\sqrt{2}L_x L_y} \sum_{\mathbf{k}\in\mathrm{MBZ}} \sin k_x
	\frac{\Im\lbrace\tilde{\Delta}_\mathbf{k}\rbrace}{\tilde{E}_\mathbf{k}} \tanh(\frac{\beta\tilde{E}_\mathbf{k}}{2})
	\label{eq:sc-wpx-self-consistency}\\
	-iw^{(p_y)} &= \frac{1}{\sqrt{2}L_x L_y} \sum_{\mathbf{k}\in\mathrm{MBZ}} \sin k_y
	\frac{\Im\lbrace\tilde{\Delta}_\mathbf{k}\rbrace}{\tilde{E}_\mathbf{k}} \tanh(\frac{\beta\tilde{E}_\mathbf{k}}{2})
	\label{eq:sc-wpy-self-consistency}
\end{align}
Of these, the singlet channel admits for non-zero fluctuations of the superconducting order parameter just in the $s^*$ and $d$ channels. This is because the gap function is inversion-symmetric and $p_\ell$ channels equations integrate it with an antisymmetric function.

Finally, the renormalized $s$-wave part, originated by the Cooper channel of $\hat H_U$ and discussed for the HM in Eq.~\eqref{appeq:sc-hm-ws-self-consistency} is given by:
\begin{equation}\label{eq:sc-ws-self-consistency}
	w^{(s)} = \frac{1}{L_x L_y} \sum_{\mathbf{k}\in\mathrm{BZ}} \frac{\tilde{\Delta}_\mathbf{k}}{\tilde{E}_\mathbf{k}} \tanh(\frac{\beta\tilde{E}_\mathbf{k}}{2})
\end{equation}
Let us now move to the computation of the contraction energy.

%Define now the non-local gap function
%\begin{equation}\label{eq:sc-ugap-self-consistency-intermediate}
%	\mathcal{V}_\mathbf{k} \equiv \sum_{\mathbf{k}'}
%	V_{\mathbf{k}\mathbf{k}'}
%	\langle
%	\hat \phi_{\mathbf{k}'}^\dagger
%	\rangle
%\end{equation}
%one gets immediately
%\begin{equation}\label{eq:sc-vgap-mft}
%	\hat H_V \simeq -\sum_\mathbf{k} \left[
%	\mathcal{V}_\mathbf{k} \hat \phi_\mathbf{k} + \mathcal{V}_\mathbf{k}^* \hat \phi_\mathbf{k}^\dagger
%	\right]	
%\end{equation}
%To assume symmetry is broken in a specific symmetry channel $\gamma$ means precisely to assume $\langle \hat \phi_\mathbf{k} \rangle \propto \varphi_\mathbf{k}^{(\gamma)}$. Of course, in Eq.~\eqref{eq:sc-ugap-self-consistency-intermediate} only the $\gamma$ component of the potential survives, implying the gap function acquires the same symmetry,
%\[
%	\mathcal{V}_\mathbf{k} \propto \sum_{\mathbf{k}'} \varphi_\mathbf{k}^{(\gamma)} \varphi_{\mathbf{k}'}^{(\gamma)*}
%	\varphi_{\mathbf{k}'}^{(\gamma)} \propto \varphi_\mathbf{k}^{(\gamma)}
%\]
%where orthonormality of the $\varphi_\mathbf{k}^{(\gamma)}$ functions of Tab.~\ref{tab:x-wave-reciprocal-factors} was used. Thus, assuming to have superconductivity in a given sector $\gamma$, the self consistency equation reads
%\begin{equation}\label{eq:sc-vgap-self-consistency}
%	\forall \gamma \in \lbrace s^*, p_x, p_y, d_{x^2-y^2} \rbrace
%	\qquad
%	\mathcal{V}_\mathbf{k}\big|_\gamma \equiv \frac{V}{2L_x L_y} \sum_\mathbf{k}
%	\varphi_\mathbf{k}^{(\gamma)}
%	\big\langle 
%		\hat \phi_\mathbf{k}^\dagger
%	\big\rangle
%\end{equation}
%Now we merge the two interaction in a single gap function.

\subsection{Cooper contraction energy}\label{subsec:sc-cooper-energy}

The Cooper contraction energy is immediately derived from Eq.~\eqref{eq:sc-Vos-cooper-double-counting},
\[
\begin{aligned}
	E_{\mathrm{C}/V/\mathrm{o.s.}}^{(\mathrm{SC})} &= - L_x L_y \times V \sum_\gamma \left[
		\frac{1}{L_x L_y} \sum_{\mathbf{q}\in\mathrm{BZ}}
		\varphi_\mathbf{q}^{(\gamma)}
		w_\mathbf{q}
	\right] \left[
		\frac{1}{L_x L_y} \sum_{\mathbf{q}'\in\mathrm{BZ}}
		\varphi_{\mathbf{q}'}^{(\gamma)+}
		w_{\mathbf{q}'}^*
	\right] \\
	&= -L_x L_y \times \sum_\gamma \big|
		w^{(\gamma)}
	\big|^2
\end{aligned}
\]
and is completed by its local counterpart of Eq.~\eqref

%\subsection{Non-local bands renormalization in the same-spin sector}\label{subsec:sc-bands-renormalization-1}
%
%In the context of antiferromagnetism (Sec.~\ref{subsec:fock-renormalization-hopping-amplitude}) we discussed the role of the non-local interaction $\hat H_V$ as a source of bands effective renormalization. One of the most interesting results was the on of Eq.~\eqref{eq:af-fock-hop-ss-renormalization}, with the hopping parameter being rigidly shifted. In the present context, we aim to treat the non-local part similarly by using immediately the aforementioned results. Start from Eq.~\eqref{eq:reciprocal-space-non-local-interaction-fock-intermediate},
%\begin{multline*}
%	V \sum_{\ev{ij}} \sum_\sigma \left[
%	\langle
%	\hat c_{i\sigma}^\dagger \hat c_{j\sigma}
%	\rangle \hat c_{j\sigma}^\dagger  \hat c_{i\sigma} + \hc
%	\right] \\
%	= \frac{2V}{L_x L_y} \sum_{\mathbf{K}, \mathbf{k}, \mathbf{k}'} \sum_\sigma \left[
%	\cos \left(
%	\delta k_x
%	\right)	+ \cos \left(
%	\delta k_y
%	\right)	
%	\right]	
%	\langle
%	\hat c_{\mathbf{K}+\mathbf{k} \sigma}^\dagger 
%	\hat c_{\mathbf{K}-\mathbf{k}' \sigma}
%	\rangle
%	\hat c_{\mathbf{K}-\mathbf{k} \sigma}^\dagger  \hat c_{\mathbf{K}+\mathbf{k}'\sigma}
%\end{multline*}
%For the BCS ground state, it is immediate to see the only relevant contribution comes from
%\[
%	\mathbf{k} = -\mathbf{k}'
%\]
%which gives the diagonal part of Eq.~\eqref{eq:reciprocal-space-non-local-interaction-fock-intermediate-2}. We are then left with (half) the result of Eq.~\eqref{eq:reciprocal-space-non-local-interaction-fock-dd-intermediate}
%\begin{equation}\label{eq:reciprocal-space-non-local-interaction-fock-dd-intermediate-su}
%	V \sum_{\ev{ij}} \sum_\sigma \left[
%	\langle
%	\hat c_{i\sigma}^\dagger \hat c_{j\sigma}
%	\rangle \hat c_{j\sigma}^\dagger  \hat c_{i\sigma} + \hc
%	\right]	= \frac{2V}{L_x L_y} \sum_{\mathbf{q}, \mathbf{q}'} \sum_\sigma \left[
%	\cos \left( \delta q_x \right) + \cos \left( \delta q_y \right)	
%	\right] \langle
%	\hat c_{\mathbf{q}\sigma}^\dagger  \hat c_{\mathbf{q}\sigma}
%	\rangle
%	\hat c_{\mathbf{q}'\sigma}^\dagger  \hat c_{\mathbf{q}'\sigma}
%\end{equation}
%Recall Eq.~\eqref{eq:coscos-symmetries-decomposition}: the structure term decomposes in harmonic waves, and this feature is particularly handy in order to decouple the $\mathbf{q}$ and $\mathbf{q}'$ parts, as we later do.
%
%{\color{tabred}
%	
%\section{Superconducting solution in the Nambu formalism}
%
%As a first approach to anisotropic SC in the Hubbard model, let us discuss the superconducting solutions in the simple scenario where crystal translational invariance is preserved and thus the system can be treated by the means of common BCS. As will be discussed, the non-local attraction acts as a source of SC in all symmetry sectors.
%
%Define the Nambu spinor\footnote{
%	Notice that the spinor is here differently defined with respect to App.~\ref{appendix:mean-field-hubbard}, where because of the HF prevalence in mean-field decoupling the spinor components were homogeneously fermions creations or destructions.
%} as in BCS
%\[
%\hat \Psi_\mathbf{k} \equiv \begin{bmatrix}
%	\hat c_{\mathbf{k}\uparrow} \\
%	\hat c_{-\mathbf{k}\downarrow}^\dagger
%\end{bmatrix}
%\]
%Evidently,
%\begin{equation}\label{eq:extended-hubbard-phi-psi-expressions}
%	\phi_\mathbf{k} = \hat \Psi_\mathbf{k}^\dagger \begin{bmatrix}
%		0 & 1 \\ 0 & 0
%	\end{bmatrix} \hat \Psi_\mathbf{k}
%	\qquad
%	\phi_\mathbf{k}^\dagger = \hat \Psi_\mathbf{k}^\dagger \begin{bmatrix}
%		0 & 0 \\ 1 & 0
%	\end{bmatrix} \hat \Psi_\mathbf{k}
%\end{equation}
%The full hamiltonian is then given by:
%\begin{equation}\label{eq:extended-hubbard-hamiltonian-nambu-bogoliubov}
%	\hat H = \sum_\mathbf{k} \hat \Psi_\mathbf{k} h_\mathbf{k} \hat \Psi_\mathbf{k}
%	\qquad
%	h_\mathbf{k} \equiv \begin{bmatrix}
%		\epsilon_\mathbf{k} & - \Delta_\mathbf{k}^* \\
%		- \Delta_\mathbf{k} & - \epsilon_\mathbf{k}
%	\end{bmatrix}
%\end{equation}
%Next step is to perform the well-known Bogoliubov transform and reduce all the problem down to a simple ensemble of quantum pseudospins.
%
%\subsection{Bogoliubov transform and pseudospins picture}\label{subsec:bogoliubov-mean-field-extended-hubbard}
%
%Let $\tau^\alpha$ for $\alpha = x,y,z$ be the Pauli matrices. Define the pseudospin operator:
%\[
%	\hat s_\mathbf{k}^\alpha \equiv \hat \Psi_\mathbf{k}^\dagger \tau^\alpha \hat \Psi_\mathbf{k}
%	\qq{for}
%	\alpha = x,y,z
%\]
%As can be shown easily, these operators realize spin-$1/2$ algebra. $\hat H$ represents an ensemble of $L_x L_y$ independent spins subject to pseudo-magnetic fields. Note that, differently form App.~\ref{app:mean-field-hubbard} where the chemical potential is inserted later (because in Nambu formalism it accounts for a diagonal term) here the chemical potential is part of the $z$ component of the pseudo-magnetic field, since
%\begin{align}
%	\hat n_{\mathbf{k}\uparrow} + \hat n_{-\mathbf{k}\downarrow} &= \hat c_{\mathbf{k}\uparrow}^\dagger \hat c_{\mathbf{k}\uparrow} + \hat c_{-\mathbf{k}\downarrow}^\dagger \hat c_{-\mathbf{k}\downarrow} \nonumber \\
%	&= \hat c_{\mathbf{k}\uparrow}^\dagger \hat c_{\mathbf{k}\uparrow} - \hat c_{-\mathbf{k}\downarrow} \hat c_{-\mathbf{k}\downarrow}^\dagger + \Id \nonumber \\
%	&=  \hat \Psi_\mathbf{k}^\dagger \tau^z \hat \Psi_\mathbf{k} + \Id \label{eq:number-operator-z-spin-relation}
%\end{align}
%and then it follows
%\[
%\begin{aligned}
%	-\mu\hat N &= -\mu \sum_{\mathbf{k} \in \mathrm{BZ}} \left[ 
%	\hat n_{\mathbf{k}\uparrow} + \hat n_{-\mathbf{k}\downarrow} 
%	\right] \\
%	&= -\mu \sum_{\mathbf{k} \in \mathrm{BZ}} \hat \Psi_\mathbf{k}^\dagger \tau^z \hat \Psi_\mathbf{k} -\mu L_x L_y
%\end{aligned}
%\]
%Then, adding a term $-\mu \hat N$ to $\hat H$, apart from an irrelevant total energy increase, changes the pseudo-field whose explicit form becomes
%\begin{equation} \label{eq:extended-hubbard-pseudo-magnetic-field}
%	\mathbf{b}_\mathbf{k} \equiv \begin{bmatrix}
%		-\Re{\Delta_\mathbf{k}} \\
%		-\Im{\Delta_\mathbf{k}} \\ \epsilon_\mathbf{k} - \mu
%	\end{bmatrix}
%\end{equation}
%This hamiltonian behaves as an ensemble of spins in local magnetic fields precisely as in Eq.~\eqref{appeq:hubbard-bogoliubov-hamiltonian-pseudofields},
%\begin{equation}\label{eq:extended-hubbard-bogoliubov-hamiltonian-pseudofields}
%	\hat H -\mu \hat N = \sum_{\mathbf{k} \in \mathrm{BZ}} \mathbf{b}_\mathbf{k} \cdot \hat{\mathbf{s}}_\mathbf{k}
%	\qq{where}
%	\hat{\mathbf{s}}_\mathbf{k} = \begin{bmatrix}
%		\hat s_\mathbf{k}^x \\
%		\hat s_\mathbf{k}^y \\
%		\hat s_\mathbf{k}^z
%	\end{bmatrix}
%\end{equation}
%Proceed as in App.~\ref{app:mean-field-hubbard} and diagonalize via a rotation,
%\[
%d_\mathbf{k} \equiv \begin{bmatrix}
%	-E_\mathbf{k} & \\ & E_\mathbf{k}
%\end{bmatrix}
%\qq{being}
%E_\mathbf{k} \equiv \sqrt{\xi_\mathbf{k}^2 + \abs{\Delta_\mathbf{k}}^2}
%\]
%and $\xi_\mathbf{k} \equiv \epsilon_\mathbf{k} - \mu$. Given the pseudoangles
%\[
%\tan(2\theta_\mathbf{k}) \equiv \frac{\abs{\Delta_\mathbf{k}}}{\xi_\mathbf{k}}
%\qquad
%\tan(2\zeta_\mathbf{k}) \equiv \frac{\Im{\Delta_\mathbf{k}}}{\Re{\Delta_\mathbf{k}}}
%\]
%the general diagonalizer will be an orthogonal rotation matrix
%\begin{align}
%	W_\mathbf{k} &= e^{i \left(\theta_\mathbf{k} - \frac{\pi}{2}\right) \tau^y} e^{i \zeta_\mathbf{k} \tau^z} \nonumber \\
%	&= \begin{bmatrix}
%		-\sin\theta_\mathbf{k}  & -\cos\theta_\mathbf{k}  \\ 
%		\cos\theta_\mathbf{k}  & -\sin\theta_\mathbf{k} 
%	\end{bmatrix} \begin{bmatrix}
%		e^{i\zeta_\mathbf{k} } & \\ & e^{-i\zeta_\mathbf{k} }
%	\end{bmatrix} \nonumber \\
%	&= \begin{bmatrix}
%		-\sin\theta_\mathbf{k}  e^{i\zeta_\mathbf{k} } & -\cos\theta_\mathbf{k}  e^{-i\zeta_\mathbf{k} }  \\ 
%		\cos\theta_\mathbf{k}  e^{i\zeta_\mathbf{k} } & -\sin\theta_\mathbf{k}  e^{-i\zeta_\mathbf{k} } 
%	\end{bmatrix} \label{eq:extended-hubbard-bogoliubov-W-diagonalizer-explicit}
%\end{align}
%given by a rotation of angle $\zeta_\mathbf{k}$ around the $z$ axis, to align the $x$ axis with the field projection onto the $xy$ plane, followed by a rotation around the $y$ axis to anti-align with the pseudo-field. 
%
%}
%
%\subsection{BCS ground state properties}
%
%The MFT-BCS solution is given by a degenerate Fermi gas at ground state, whose quasi-particles occupy two bands $\pm E_\mathbf{k}$ and their fermionic operators are given by
%\[
%	\hat \gamma_\mathbf{k}^{(-)} \equiv \left[
%		W_\mathbf{k} \hat \Psi_\mathbf{k}
%	\right]_1
%	\qquad
%	\hat \gamma_\mathbf{k}^{(+)} \equiv \left[
%		W_\mathbf{k} \hat \Psi_\mathbf{k}
%	\right]_2
%\]
%The diagonalization operators are given by
%\[
%	\hat\Gamma_\mathbf{k} \equiv W_\mathbf{k} \hat\Psi_\mathbf{k}
%	\qq{where}
%	\hat\Gamma_\mathbf{k} = \begin{bmatrix}
%		\hat \gamma_\mathbf{k}^{(-)} \\ \hat \gamma_\mathbf{k}^{(+)}
%	\end{bmatrix}
%\]
%Using Eq.~\eqref{appeq:finite-temperature-order-parameter-derivation-intermediate}, 
%\[
%	\left\langle [\hat \Psi_\mathbf{k}^\dagger]_i [\hat \Psi_\mathbf{k}]_j \right\rangle = [W_\mathbf{k}]_{1 i} [W_\mathbf{k}^\dagger]_{j 1} f\left( -E_\mathbf{k}; \beta,0 \right) + [W_\mathbf{k}]_{2 i} [W_\mathbf{k}^\dagger]_{j 2} f\left( E_\mathbf{k}; \beta,0 \right)
%\]
%where in the Fermi-Dirac function chemical potential was set to zero, because it already was included in the diagonalized hamiltonian.
%Recalling Eq.~\eqref{eq:extended-hubbard-phi-psi-expression}, it follows for $i=1$, $j=2$
%\begin{align}
%	\langle \hat \phi_\mathbf{k}^\dagger \rangle &= [W_\mathbf{k}]_{11} [W_\mathbf{k}^\dagger]_{21} f\left( -E_\mathbf{k}; \beta,0 \right) + [W_\mathbf{k}]_{21} [W_\mathbf{k}^\dagger]_{22} f\left( E_\mathbf{k}; \beta,0 \right) \label{eq:pairing-dagger-expectation-algorithmic} \\
%	&= \frac{1}{2} \sin \left(
%	2 \theta_\mathbf{k}
%	\right) e^{i 2 \zeta_\mathbf{k}} \tanh(\frac{\beta E_\mathbf{k}}{2}) \label{eq:pairing-dagger-expectation-theoretical}
%\end{align}
%The last passage has been obtained by computing the matrix element from the explicit form of $W_\mathbf{k}$ of Eq.~\eqref{eq:extended-hubbard-bogoliubov-W-diagonalizer-explicit} and by the simple relation
%\[
%\begin{aligned}
%	\frac{1}{e^{-x}+1} - \frac{1}{e^x+1} &= \frac{e^x -1}{e^x +1} \\
%	&= \tanh(\frac{x}{2})
%\end{aligned}
%\]
%Similarly, for $i=1$, $j=1$
%{\color{tabred}
%\begin{align}
%	\langle \hat c_{\mathbf{k}\uparrow}^\dagger \hat c_{\mathbf{k}\uparrow} \rangle &= [W_\mathbf{k}]_{11} [W_\mathbf{k}^\dagger]_{11} f\left( -E_\mathbf{k}; \beta,0 \right) + [W_\mathbf{k}]_{21} [W_\mathbf{k}^\dagger]_{12} f\left( E_\mathbf{k}; \beta,0 \right) \label{eq:number-dagger-expectation-algorithmic-11} \\
%	&= \sin^2 \theta_\mathbf{k} f\left( -E_\mathbf{k}; \beta,0 \right) + \cos^2 \theta_\mathbf{k} f\left( E_\mathbf{k}; \beta,0 \right) \nonumber \\
%	&= \sin^2 \theta_\mathbf{k} \tanh(\frac{\beta E_\mathbf{k}}{2}) + f\left( E_\mathbf{k}; \beta,0 \right)
%	\label{eq:number-dagger-expectation-theoretical-11}
%\end{align}
%and for $i=2$, $j=2$
%\begin{align}
%	\langle \hat c_{-\mathbf{k}\downarrow} \hat c_{-\mathbf{k}\downarrow}^\dagger \rangle &= [W_\mathbf{k}]_{12} [W_\mathbf{k}^\dagger]_{21} f\left( -E_\mathbf{k}; \beta,0 \right) + [W_\mathbf{k}]_{22} [W_\mathbf{k}^\dagger]_{22} f\left( E_\mathbf{k}; \beta,0 \right) \label{eq:number-dagger-expectation-algorithmic-22} \\
%	&= \cos^2 \theta_\mathbf{k} f\left( -E_\mathbf{k}; \beta,0 \right) + \sin^2 \theta_\mathbf{k} f\left( E_\mathbf{k}; \beta,0 \right) \nonumber \\
%	&= \cos^2 \theta_\mathbf{k} \tanh(\frac{\beta E_\mathbf{k}}{2}) + f\left( E_\mathbf{k}; \beta,0 \right)
%	\label{eq:number-dagger-expectation-theoretical-22}
%\end{align}}
%
%\paragraph{Gap function.} Eqns.~\eqref{eq:pairing-dagger-expectation-algorithmic}, \eqref{eq:pairing-dagger-expectation-theoretical} give us both the algorithmic formula (first row) and its theoretical counterpart (second row) to compute the order parameters in the HF approach at each point in $k$-space $(k_x,k_y)$. We can finally derive the BCS self-consistency equation
%\begin{align}
%	\Delta_\mathbf{k} &\equiv \frac{1}{2} \sum_{\mathbf{k}'}
%	\left[
%	V^{(s)} +
%	V_{\mathbf{k}\mathbf{k}'}
%	\right] \frac{\abs{\Delta_{\mathbf{k}'}}}{\sqrt{\xi_{\mathbf{k}'}^2 + \abs{\Delta_{\mathbf{k}'}}^2}} \exp{i \arctan(\frac{\Im{\Delta_{\mathbf{k}'}}}{\Re{\Delta_{\mathbf{k}'}}})} \tanh(\frac{\beta}{2} \sqrt{\xi_{\mathbf{k}'}^2 + \abs{\Delta_{\mathbf{k}'}}^2}) \nonumber \\
%	&= \frac{1}{2} \sum_{\mathbf{k}'}
%	\left[
%	V^{(s)} +
%	V_{\mathbf{k}\mathbf{k}'}
%	\right] \frac{\Delta_{\mathbf{k}'}}{\sqrt{\xi_{\mathbf{k}'}^2 + \abs{\Delta_{\mathbf{k}'}}^2}} \tanh(\frac{\beta}{2} \sqrt{\xi_{\mathbf{k}'}^2 + \abs{\Delta_{\mathbf{k}'}}^2}) 
%	\label{eq:self-consistency-equation-theoretical}
%\end{align}
%The whole point of the HF algorithm is to find an iterative solution for each symmetry channel, using the self-consistency equation projection of Tab.~\ref{tab:x-wave-self-consistency-equation}.
%
%\paragraph{System density.} The $z$ component of the spin operators is related to density: using Eq.~\eqref{appeq:finite-temperature-order-parameter-derivation-intermediate},
%\[
%	\langle
%	\hat\Psi_\mathbf{k}^\dagger \tau^z \hat\Psi_\mathbf{k}
%	\rangle = \left\langle 
%	[\hat \Psi_\mathbf{k}^\dagger]_1 [\hat \Psi_\mathbf{k}]_1 
%	\right\rangle - \left\langle 
%	[\hat \Psi_\mathbf{k}^\dagger]_2 [\hat \Psi_\mathbf{k}]_2
%	\right\rangle
%\]
%Proceed as previously, and from Eq.~\eqref{eq:number-operator-z-spin-relation},
%\begin{align}
%	\langle \hat n_{\mathbf{k}\uparrow} \rangle + \langle \hat 	n_{-\mathbf{k}\downarrow} \rangle = 1 &+ \langle \hat\Psi_\mathbf{k}^\dagger \tau^z \hat\Psi_\mathbf{k} \rangle \nonumber \\
%	= 1 &+ \left(
%	\abs{[W_\mathbf{k}]_{11}}^2 - \abs{[W_\mathbf{k}]_{12}}^2
%	\right) f\left( -E_\mathbf{k}; \beta,0 \right) \nonumber \\
%	&+ \left(
%	\abs{[W_\mathbf{k}]_{21}}^2 - \abs{[W_\mathbf{k}]_{22}}^2
%	\right) f\left( E_\mathbf{k}; \beta,0 \right) \label{eq:density-expectation-algorithmic} \\
%	= 1 &- \cos \left(
%	2 \theta_\mathbf{k}
%	\right) \tanh(\frac{\beta E_\mathbf{k}}{2}) \label{eq:density-expectation-theoretical} 
%\end{align}
%coherently with Eqns.~\eqref{eq:number-dagger-expectation-theoretical-11} and \eqref{eq:number-dagger-expectation-theoretical-22}. The expectation value for the density is needed in order to extract the optimal chemical potential $\mu$ for the target density we aim to simulate at the given parametrization. This is numerically obtained by using Eq.~\eqref{eq:density-expectation-algorithmic} directly on the diagonalization matrix of $h_\mathbf{k}$.
%
%\paragraph{Ground state at zero temperature.} 
%Let $\beta \to +\infty$. The basic BCS grond state is well known and identical in the present discussion. It is easily obtained by considering the zero-temperature ground state of the pseudospin hamiltonian of Eq.~\eqref{eq:extended-hubbard-hamiltonian-nambu-bogoliubov},
%\begin{equation}\label{eq:bcs-state-2theta}
%	\ket{\mathrm{BCS}} = \bigotimes_\mathbf{k} \ket{2\theta_\mathbf{k}}
%\end{equation}
%where $\ket{2\theta_\mathbf{k}}$ is the up-state for the $\mathbf{k}$-th rotated pseudospin operator $\hat \Gamma_\mathbf{k}^\dagger \tau^z \hat \Gamma_\mathbf{k}$ (consider a diagram analogous to Fig.~\ref{fig:pseudo-magnetic-field}). Said state can be expressed, making use of the non-rotated pseudospin operator $\hat \Psi_\mathbf{k}^\dagger \tau^z \hat \Psi_\mathbf{k}$ up and down states
%\[
%	\text{up: } \ket{\Uparrow_\mathbf{k}}
%	\qquad
%	\text{down: } \ket{\Downarrow_\mathbf{k}}
%\]
%by the means of a simple Bloch's representation {\color{tabred}[Redo this computation...]},
%\begin{equation}\label{eq:2theta-down-up}
%	\ket{2\theta_\mathbf{k}} = \cos \theta_\mathbf{k} \ket{\Downarrow_\mathbf{k}} - \sin \theta_\mathbf{k} \ket{\Uparrow_\mathbf{k}}
%\end{equation}
%Due to Eq.~\eqref{eq:number-operator-z-spin-relation} it holds
%\[
%\begin{aligned}
%	\left[ \hat \Psi_\mathbf{k}^\dagger \tau^z \hat \Psi_\mathbf{k}  + \Id \right] \ket{\Uparrow_\mathbf{k}} &= 2\ket{\Uparrow_\mathbf{k}}
%	&&\implies
%	&&\ket{\Uparrow_\mathbf{k}}=-\hat\phi_\mathbf{k}^\dagger\ket{\Omega_\mathbf{k}} \\
%	\left[ \hat \Psi_\mathbf{k}^\dagger \tau^z \hat \Psi_\mathbf{k}  + \Id \right] \ket{\Downarrow_\mathbf{k}} &= 0
%	&&\implies
%	&&\ket{\Downarrow_\mathbf{k}}=\ket{\Omega_\mathbf{k}} 
%\end{aligned}	
%\]
%being $\ket{\Omega_\mathbf{k}}$ the local electron vacuum,
%\[
%	\ket{\Omega} = \bigotimes_\mathbf{k} \ket{\Omega_\mathbf{k}}
%\]
%Taking Eq.~\eqref{eq:bcs-state-2theta}, combined with Eq.~\eqref{eq:2theta-down-up}, we get
%\begin{align}
%	\ket{\mathrm{BCS}} &= \bigotimes_\mathbf{k} \left[
%		\cos \theta_\mathbf{k} \ket{\Downarrow_\mathbf{k}} - \sin \theta_\mathbf{k} \ket{\Uparrow_\mathbf{k}}
%	\right] \nonumber \\
%	&= \bigotimes_\mathbf{k} \left[
%		\cos \theta_\mathbf{k} + \sin \theta_\mathbf{k} \hat\phi_\mathbf{k}^\dagger
%	\right] \ket{\Omega_\mathbf{k}} \label{eq:bcs-state}
%\end{align}
%which is the well-known coherent BCS state.
%
%{\color{tabred}
%\subsection{Renormalization of the bare bands}\label{subsec:sc-bands-renormalization-2} 
%
%We now deal with the renormalization of bare bands anticipated in Sec.~\ref{subsec:sc-bands-renormalization-1}. Taking together Eqns.~\eqref{eq:reciprocal-space-non-local-interaction-fock-dd-intermediate-su}, \eqref{eq:pairing-dagger-expectation-algorithmic} and \eqref{eq:pairing-dagger-expectation-theoretical} we get:
%\begin{multline}
%	V \sum_{\ev{ij}} \sum_\sigma \left[
%	\langle
%	\hat c_{i\sigma}^\dagger \hat c_{j\sigma}
%	\rangle \hat c_{j\sigma}^\dagger  \hat c_{i\sigma} + \hc
%	\right]
%	= \frac{2V}{L_x L_y} \sum_{\mathbf{q}, \mathbf{q}'} \left[
%	\cos \left( \delta q_x \right) + \cos \left( \delta q_y \right)	
%	\right] \\
%	\times \bigg[
%		\left(
%			\sin^2 \theta_\mathbf{q} \tanh(\frac{\beta E_\mathbf{q}}{2}) + f\left( E_\mathbf{q}; \beta,0 \right) 
%		\right)
%		\hat c_{\mathbf{q}'\uparrow}^\dagger \hat c_{\mathbf{q}'\uparrow} \\
%		+ \left(
%			 1 - \cos^2 \theta_{-\mathbf{q}} \tanh(\frac{\beta E_{-\mathbf{q}}}{2}) - f\left( E_{-\mathbf{q}}; \beta,0 \right)
%		\right)
%		\hat c_{\mathbf{q}'\downarrow}^\dagger \hat c_{\mathbf{q}'\downarrow}
%	\bigg]
%	\label{eq:reciprocal-space-non-local-interaction-fock-dd-intermediate-sc-2}
%\end{multline}
%Spatial inversion symmetry guarantees
%\[
%	\cos^2 \theta_{-\mathbf{q}} = \cos^2 \theta_\mathbf{q}
%	\qq{as well as}
%	E_{-\mathbf{q}} = E_\mathbf{q}
%\]
%By simple algebraic manipulation is easy to see:
%\[
%\begin{aligned}
%	1 - \cos^2 \theta_\mathbf{q} \tanh(\frac{\beta E_\mathbf{q}}{2}) - f\left( E_\mathbf{q}; \beta,0 \right) &= \sin^2 \theta_\mathbf{q} \tanh(\frac{\beta E_\mathbf{q}}{2}) + 1 - \tanh(\frac{\beta E_\mathbf{q}}{2}) - f\left( E_\mathbf{q}; \beta,0 \right) \\
%	&= \sin^2 \theta_\mathbf{q} \tanh(\frac{\beta E_\mathbf{q}}{2}) + f\left( E_\mathbf{q}; \beta,0 \right)
%\end{aligned}
%\]
%Since
%\[
%	1 - \tanh(\frac x 2) - \frac{1}{e^x+1} = \frac{1}{e^x+1}
%\]
%Use now:
%\[
%\begin{aligned}
%	\sin^2 \theta_\mathbf{q} &= \frac{1 - \cos(2\theta_\mathbf{q})}{2} \\
%	&= \frac 1 2 - \frac{\xi_\mathbf{q}}{2\sqrt{\xi_\mathbf{q}^2 + \abs{\Delta_\mathbf{q}}^2}}
%\end{aligned}
%\]
%and let:
%\[
%	g_\mathbf{q} \equiv \left[ 
%		\frac 1 2 - \frac{\xi_\mathbf{q}}{2\sqrt{\xi_\mathbf{q}^2 + \abs{\Delta_\mathbf{q}}^2}}
%	\right] \tanh(\frac{\beta}{2} \sqrt{\xi_\mathbf{q}^2 + \abs{\Delta_\mathbf{q}}^2}) + f\left(\sqrt{\xi_\mathbf{q}^2 + \abs{\Delta_\mathbf{q}}^2}; \beta,0 \right)
%\]
%which further simplifies to
%\begin{equation}\label{eq:sc-bands-renormalization-gq-definition}
%	g_\mathbf{q} \equiv
%	\frac 1 2 - \frac{\xi_\mathbf{q}}{2\sqrt{\xi_\mathbf{q}^2 + \abs{\Delta_\mathbf{q}}^2}}
%	\tanh(\frac{\beta}{2} \sqrt{\xi_\mathbf{q}^2 + \abs{\Delta_\mathbf{q}}^2})
%\end{equation}
%
%Thus, the original o.s. Fock term retrieved from Wick's theorem on the EHM reduces to
%\[
%	V \sum_{\ev{ij}} \sum_\sigma \left[
%	\langle
%	\hat c_{i\sigma}^\dagger \hat c_{j\sigma}
%	\rangle \hat c_{j\sigma}^\dagger  \hat c_{i\sigma} + \hc
%	\right]
%	= \frac{2V}{L_x L_y} \sum_{\mathbf{q}, \mathbf{q}'} \sum_\sigma \left[
%		\cos \left( \delta q_x \right) + \cos \left( \delta q_y \right)	
%	\right] g_\mathbf{q} \hat c_{\mathbf{q}'\sigma}^\dagger \hat c_{\mathbf{q}'\sigma}
%\]
%Recall now the result of Eq.~\eqref{eq:coscos-symmetries-decomposition},
%\[
%	\cos \left( \delta q_x \right)	+ \cos \left( \delta q_y  \right) = \frac 1 2 \sum_\gamma \varphi_\mathbf{q}^{(\gamma)} \varphi_{\mathbf{q}'}^{(\gamma)*}
%	\qq{for $\gamma \in \lbrace s^*, p_x, p_y, d_{x^2-y^2} \rbrace$}
%\]
%which gives (sum over $\gamma$ is intended within the aforementioned symmetries)
%\begin{equation}\label{eq:reciprocal-space-non-local-interaction-fock-dd-intermediate-sc-3}
%	\frac{2V}{L_x L_y} \sum_{\mathbf{q}, \mathbf{q}'} \sum_\sigma \left[
%	\cos \left( \delta q_x \right) + \cos \left( \delta q_y \right)	
%	\right] g_\mathbf{q} \hat c_{\mathbf{q}'\sigma}^\dagger \hat c_{\mathbf{q}'\sigma} = \frac{V}{L_x L_y} \sum_{\mathbf{q}, \mathbf{q}'} \sum_{\sigma,\gamma} \varphi_\mathbf{q}^{(\gamma)} \varphi_{\mathbf{q}'}^{(\gamma)*} g_\mathbf{q} \hat c_{\mathbf{q}'\sigma}^\dagger \hat c_{\mathbf{q}'\sigma}
%\end{equation}
%Evidently from Eq.~\eqref{eq:sc-bands-renormalization-gq-definition}, $g_\mathbf{q}$ is an even function of the momentum, a feature that ensures
%\[
%	\frac{1}{L_xL_y} \sum_\mathbf{q} \varphi_\mathbf{q}^{(p_\ell)} g_\mathbf{q} = 0
%	\qq{for $\ell \in \left\lbrace x,y \right\rbrace$}
%\]
%
%\paragraph{General result.} Let us now divide the discussion in two parts. First, let us deal with the theoretical general result of the above calculations. Define the $s^*$ and $d_{x^2-y^2}$ components as
%\[
%	g^{(s^*)} \equiv \frac{1}{L_xL_y} \sum_\mathbf{q} (\cos q_x + \cos q_y) g_\mathbf{q} 
%	\qquad
%	g^{(d)} \equiv \frac{1}{L_xL_y} \sum_\mathbf{q} (\cos q_x - \cos q_y) g_\mathbf{q}
%\]
%and from Eq.~\eqref{eq:reciprocal-space-non-local-interaction-fock-dd-intermediate-sc-3}  we get the final form
%\begin{multline}
%	\frac{2V}{L_x L_y} \sum_{\mathbf{q}, \mathbf{q}'} \sum_\sigma \left[
%	\cos \left( \delta q_x \right) + \cos \left( \delta q_y \right)	
%	\right] g_\mathbf{q} \hat c_{\mathbf{q}'\sigma}^\dagger \hat c_{\mathbf{q}'\sigma} \\
%	= V \sum_{\mathbf{q}\sigma} 
%	\left[
%		g^{(s^*)} (\cos q_x + \cos q_y) + g^{(d)} (\cos q_x - \cos q_y)
%	\right] \hat c_{\mathbf{q}\sigma}^\dagger \hat c_{\mathbf{q}\sigma} \label{eq:reciprocal-space-non-local-interaction-fock-dd-intermediate-sc-4}
%\end{multline}
%This equation reduces fully the initial o.s. Fock component of $\hat H_V$ to a simpler, decoupled form. Here, similarly to what we observed for AF phase in Sec.~\ref{subsec:fock-renormalization-hopping-amplitude}, the bare bands are renormalized,
%\begin{equation}\label{eq:sc-bands-renormalization-general}
%	\tilde{\epsilon}_\mathbf{k} \equiv \epsilon_\mathbf{k} + V\left[
%		g^{(s^*)} (\cos k_x + \cos k_y) + g^{(d)} (\cos k_x - \cos k_y)
%	\right]
%\end{equation}
%As is done in next paragraph, the $s^*$ is actually a rigid $t$ renormalization, which however requires a little care.
%
%\paragraph{Pure $x$-wave superconductivity.}
%
%As long as we work in a precise sector ($s\oplus s^*$ as well as $d_{x^2-y^2}$) with a gap function completely contained in said symmetry sector, we can rule out the $d_{x^2-y^2}$-wave component of $g_\mathbf{q}$ from Eq.~\eqref{eq:sc-bands-renormalization-general}
%\[
%	\frac{1}{L_xL_y} \sum_\mathbf{q} \varphi_\mathbf{q}^{(d)} g_\mathbf{q} = 0
%\]
%The result above is valid only if $\Delta_\mathbf{q}$ is described only by a single symmetry harmonics. This is because under a rotation of angle $\pi/2$ the two functions behave differently:
%\[
%	(q_x, q_y) \to (-q_y, q_x)
%	\quad\colon\quad
%	\begin{cases}
%		\varphi_\mathbf{q}^{(d)} \to - \varphi_\mathbf{q}^{(d)} \\
%		g_\mathbf{q} \to g_\mathbf{q}
%	\end{cases}
%\]
%The only remainder of Eq.~\eqref{eq:sc-bands-renormalization-general} is its $s^*$ part
%\begin{equation}\label{eq:sc-bands-renormalization-xwave}
%	\tilde{\epsilon}_\mathbf{k} \equiv \epsilon_\mathbf{k} + V	g^{(s^*)} (\cos k_x + \cos k_y)
%\end{equation}
%and since $\epsilon_\mathbf{k} = -2t(\cos k_x + \cos k_y)$ we obtain an equation essentially identical to the one expressing the hopping renormalization in the AF phase, Eq.~\eqref{eq:af-fock-hop-ss-renormalization}. Indeed, let $w \equiv g^{(s^*)}/2$ be the new HF parameter, we get
%\begin{equation}\label{eq:sc-fock-hop-ss-renormalization}
%	\tilde{t} \equiv t - wV
%\end{equation}
%Once again the hopping parameter shift is rigid and controlled directly by $V$. As done for the AF phase, we will denote the new bands as:
%\[
%	\xi_\mathbf{k} \to \tilde{\xi}_\mathbf{k}
%	\qquad 
%	E_\mathbf{k} \to \tilde{E}_\mathbf{k}
%\]}

\section{Full MFT hamiltonian and anisotropic pairing}\label{sec:sc-full-hamiltonian}

By composing all three channels we are able to derive the final form of the MFT gran-canonical hamiltonian,
\begin{multline*}
	\hat H - \mu \hat N \simeq \sum_{\mathbf{k}\in\mathrm{MBZ}} \tilde{\xi}_{\mathbf{k}\sigma} \left[
		\hat c_{\mathbf{k}\uparrow}^\dagger
		\hat c_{\mathbf{k}\uparrow} +
		\hat c_{-\mathbf{k}\downarrow}
		\hat c_{-\mathbf{k}\downarrow}^\dagger
	\right] - \sum_\sigma \sum_{\mathbf{k}\in\mathrm{BZ}} \left[
		\tilde{\Delta}_\mathbf{k}
		\hat \phi_\mathbf{k} + \tilde{\Delta}_\mathbf{k}^* \hat \phi_\mathbf{k}^\dagger
	\right] \\ - \left[
		E_{\mathrm{A}/t}^{(\mathrm{SC})} +
		E_{\mathrm{H}/U}^{(\mathrm{SC})} +		E_{\mathrm{C}/U}^{(\mathrm{SC})} +
		E_{\mathrm{H}/V}^{(\mathrm{SC})} + E_{\mathrm{F}/V}^{(\mathrm{SC})} + E_{\mathrm{C}/V/\mathrm{o.s.}}^{(\mathrm{SC})}
	\right]
\end{multline*}
having we included the ``anticommutation energy'' also defined for the conventional HM in Eq.~\eqref{appeq:sc-hm-anticommutation-energy},
\[
	E_{\mathrm{A}/t}^{(\mathrm{SC})} \equiv -\sum_{\mathbf{k}\in\mathrm{BZ}} \tilde{\xi}_\mathbf{k}
\]
coming from fermionic anticommutation relations that are employed in order to get the kinetic term. The renormalized bands are
\[
	\tilde{\xi}_{\mathbf{k}\sigma} = \epsilon_{\mathbf{k}\sigma} + V \sum_{\gamma\in\lbrace s^*,d \rbrace} u^{(\gamma)} \varphi_{\mathbf{k}}^{(\gamma)*} - \tilde{\mu}
\]
and the full gap function by
\[
	\tilde{\Delta}_{\mathbf{k}\sigma} = -Uw^{(s)} + V \sum_{\gamma} w^{(\gamma)} \varphi_\mathbf{k}^{(\gamma)*}
\]
We can identify the gap harmonics by
\[
	\Delta^{(s)} = -U w^{(s)}
	\qquad
	\Delta^{(\gamma)} = V w^{(\gamma)}
	\qq{being}
	\gamma\in\lbrace s^*, p_x, p_y, d \rbrace
\]

{\color{tabred}

Define the full gap function as the sum of both contributions,
\begin{equation}\label{eq:sc-os-gap-function-definition}
	\Delta_\mathbf{k} \equiv \mathcal{V}_\mathbf{k} - \mathcal{U}_\mathbf{k}
\end{equation}
The full self-consistency equation is given by the simple combination of Eqns.~\eqref{eq:sc-ugap-self-consistency} and \eqref{eq:sc-vgap-self-consistency},
\begin{equation}\label{eq:self-consistency-equation}
	\Delta_\mathbf{k} \equiv \sum_{\mathbf{k}'}
	\left[
	V^{(s)} +
	V_{\mathbf{k}\mathbf{k}'}
	\right]
	\langle
	\hat \phi_{\mathbf{k}'}^\dagger
	\rangle
	\qq{with}
	V^{(s)} = - \frac{U}{2L_xL_y}
\end{equation}
The gap function decomposes in symmetry channels as well,
\[
\Delta_\mathbf{k} = \sum_\gamma \Delta^{(\gamma)} \varphi_\mathbf{k}^{(\gamma)}
\]
If SC arises in a specific symmetry channel, $\Delta_\mathbf{k}$ will show the same symmetry. It follows, due to orthonormality and using Eq.~\eqref{eq:self-consistency-equation},
\begin{align}
	\Delta^{(\gamma)} &= \frac{1}{L_xL_y} \sum_{\mathbf{k}} \varphi_\mathbf{k}^{(\gamma)*} \Delta_\mathbf{k} \nonumber \\
	&= \frac{1}{L_xL_y} \sum_{\mathbf{k}} \varphi_\mathbf{k}^{(\gamma)*} \sum_{\mathbf{k}'}
	\left[
	V^{(s)} +
	V_{\mathbf{k}\mathbf{k}'}
	\right]
	\langle
	\hat \phi_{\mathbf{k}'}^\dagger
	\rangle \nonumber \\
	&= \frac{1}{L_xL_y} \sum_{\mathbf{k}} \varphi_\mathbf{k}^{(\gamma)*} \sum_{\mathbf{k}'\gamma'}
	V^{(\gamma')} \varphi_\mathbf{k}^{(\gamma')} \varphi_{\mathbf{k}'}^{(\gamma')*}
	\langle
	\hat \phi_{\mathbf{k}'}^\dagger
	\rangle \nonumber \\
	&= V^{(\gamma)} \sum_{\mathbf{k}} \varphi_\mathbf{k}^{(\gamma)*} \langle
	\hat \phi_{\mathbf{k}}^\dagger
	\rangle \label{eq:self-consistency-equation-explicit}
\end{align}
This result provides a set of self-consistency equations for each symmetry channel, listed in Tab.~\ref{tab:x-wave-self-consistency-equation}. Notice that to reconstruct self-consistently the full $s$-wave phase transition, the actual gap function is given by
\[
\Delta^{(s)} + \Delta^{(s^*)} (c_x + c_y)
\]
The $s$-wave transition is the only one equipped of both the local and the non-local parts.

\setlength{\extrarowheight}{1em}
\begin{table}
	\centering
	\begin{tabular}{r E l l}
		\textbf{Structure} & \multicolumn{2}{c}{\textbf{Self-consistency equation}} & \textbf{Graph} \\
		\midrule
		$s$-wave & $\Delta^{(s)}$ & $\displaystyle -\frac{U}{2L_xL_y} \sum_{\mathbf{k}} \langle
		\hat \phi_{\mathbf{k}}^\dagger
		\rangle $ & Fig.~\ref{subfig:s-wave-correlator} \\
		Extended $s$-wave & $\Delta^{(s^*)}$ & $\displaystyle \frac{V}{L_xL_y} \sum_{\mathbf{k}} (c_x + c_y) \langle
		\hat \phi_{\mathbf{k}}^\dagger
		\rangle$ & Fig.~\ref{subfig:s*-wave-correlator} \\
		$p_x$-wave & $\Delta^{(p_x)}$ & $\displaystyle - i\sqrt{2} \frac{V}{L_xL_y} \sum_{\mathbf{k}} s_x \langle
		\hat \phi_{\mathbf{k}}^\dagger
		\rangle$ & Fig.~\ref{subfig:px-wave-correlator} \\
		$p_y$-wave & $\Delta^{(p_y)}$ & $\displaystyle -i \sqrt{2} \frac{V}{L_xL_y} \sum_{\mathbf{k}} s_y \langle
		\hat \phi_{\mathbf{k}}^\dagger
		\rangle$ & Fig.~\ref{subfig:py-wave-correlator} \\
		$d_{x^2-y^2}$-wave & $\Delta^{(d)}$ & $\displaystyle \frac{V}{L_xL_y} \sum_{\mathbf{k}} (c_x - c_y) \langle
		\hat \phi_{\mathbf{k}}^\dagger
		\rangle$ & Fig.~\ref{subfig:d-wave-correlator} \\
		\midrule
	\end{tabular}
	\caption{Symmetry resolved self-consistency equations for the MFT parameters $\Delta^{(\gamma)}$, based on Eq.~\eqref{eq:self-consistency-equation} and \eqref{eq:self-consistency-equation-explicit}. By computing $\langle \hat \phi_{\mathbf{k}}^\dagger \rangle$, it is possible to reconstruct the various components of the gap function.}
	\label{tab:x-wave-self-consistency-equation}
\end{table}
\setlength{\extrarowheight}{0em}
}

\section{SU free energy density}\label{sec:sc-free-energy}

BCS essentially relies on the insurgence of an effective free fermionic field, described by the Bogoliubov bands, and the condensation of Cooper pairs. Superconducting state is favored by the lowering of free energy granted by the shifting of much of the spectral weight to a lower-energy maximum \cite{zhou1992density}. ``Condensation energy'' is simply the energy difference between the superconducting state and the normal state, and its negativity indicates instability towards superconducting order. It's pretty straightforward to derive the ground state energy for the standard BCS state. When performing Wick's contractions,
\[
\begin{aligned}
	\langle \hat c_\alpha^\dagger \hat c_\beta^\dagger \hat c_\gamma \hat c_\delta \rangle 
	&\sim 
	\langle \hat c_\alpha^\dagger \hat c_\beta^\dagger \rangle  \hat c_\gamma \hat c_\delta
	+
	\hat c_\alpha^\dagger \hat c_\beta^\dagger \langle \hat c_\gamma \hat c_\delta \rangle 
	-
	\langle \hat c_\alpha^\dagger \hat c_\beta^\dagger \rangle 
	\langle \hat c_\gamma \hat c_\delta \rangle
	&&\text{Cooper terms}
	\\
	&-
	\langle \hat c_\alpha^\dagger \hat c_\gamma \rangle \hat c_\beta^\dagger \hat c_\delta
	-
	\hat c_\alpha^\dagger \hat c_\gamma \langle \hat c_\beta^\dagger \hat c_\delta \rangle 
	+
	\langle \hat c_\alpha^\dagger \hat c_\gamma \rangle 
	\langle \hat c_\beta^\dagger \hat c_\delta \rangle
	&&\text{Fock terms} \\
	&+
	\langle \hat c_\alpha^\dagger \hat c_\delta \rangle \hat c_\beta^\dagger \hat c_\gamma
	+
	\hat c_\alpha^\dagger \hat c_\delta \langle \hat c_\beta^\dagger \hat c_\gamma \rangle 
	-
	\langle \hat c_\alpha^\dagger \hat c_\delta \rangle 
	\langle \hat c_\beta^\dagger \hat c_\gamma \rangle
	&&\text{Hartree terms}
\end{aligned}
\]
Form each of the three rows above, the last term is the "leftover" part which shifts energy. Thus it can be ignored in derivation, but becomes important when considering the energy in the end. The EHM hamiltonian can be written as:
\begin{multline}
	\hat H = \sum_{\mathbf{k}} \xi_\mathbf{k} \left[
		\hat c_{\mathbf{k}\uparrow}^\dagger \hat c_{\mathbf{k}\uparrow} + \Id - 
		\hat c_{-\mathbf{k}\downarrow} \hat c_{-\mathbf{k}\downarrow}^\dagger 
	\right] - \sum_{\mathbf{k},\mathbf{k}'} \left[ 
		V^{(s)} + V_{\mathbf{k}\mathbf{k}'}
	\right] \hat \phi_\mathbf{k}^\dagger \hat \phi_{\mathbf{k}'} \\
	- \frac{2V}{L_x L_y} \sum_{\mathbf{k}, \mathbf{k}'} \sum_\sigma \left[
	\cos \left( \delta k_x \right) + \cos \left( \delta k_y \right)	
	\right] \hat n_{\mathbf{k}\sigma} \hat n_{\mathbf{k}'\sigma} \label{eq:pre-mft-ehm-cooper-filtered}
\end{multline}
as in Eq.~\eqref{eq:self-consistency-equation}. Following the scheme above, the ``leftovers'' of the MFT hamiltonian are just
\[
	\sum_{\mathbf{k},\mathbf{k}'} \Delta_\mathbf{k} \langle \hat \phi_{\mathbf{k}'} \rangle - \frac{2V}{L_x L_y} \sum_{\mathbf{k}, \mathbf{k}'} \sum_\sigma \left[
	\cos \left( \delta k_x \right) + \cos \left( \delta k_y \right)	
	\right] g_\mathbf{k} g_{\mathbf{k}'}
\]
Further developing this result and applying Eqns.~\eqref{eq:pairing-dagger-expectation-theoretical}, \eqref{eq:coscos-symmetries-decomposition}, these last terms can be written as:
\begin{equation}\label{eq:sc-free-energy-leftovers}
	\sum_\mathbf{k} \frac{\abs{\Delta_\mathbf{k}}^2}{2\tilde{E}_\mathbf{k}} \tanh(\frac{\beta \tilde{E}_\mathbf{k}}{2}) - 2V L_x L_y \sum_\gamma \big| g^{(\gamma)} \big|^2
	\qquad
	\gamma\in\lbrace s^*, d_{x^2-y^2} \rbrace
\end{equation}
as for Eq.~\eqref{eq:reciprocal-space-non-local-interaction-fock-dd-intermediate-sc-4}. Notice the presence of a volume factor in the $\mathcal{O}\left(g^2\right)$ correction.

Now, we retrieve the expression for the MFT free energy density \cite{hutchinson2021mixed} simply by adding four contributions:
\begin{enumerate}
	\item Bogoliubov free quasiparticles thermal ground state energy density,
	\[
	\begin{aligned}
		\frac{1}{L_x L_y} \sum_\mathbf{k} \tilde{E}_\mathbf{k} \left[
			 f( \tilde{E}_\mathbf{k}; \beta,0 ) - f( - \tilde{E}_\mathbf{k}; \beta,0 )
		\right] &= \frac{1}{L_x L_y} \sum_\mathbf{k} \tilde{E}_\mathbf{k} \left[
			f( \tilde{E}_\mathbf{k}; \beta,0 ) - \left( 
				1-  f( \tilde{E}_\mathbf{k}; \beta,0 )
			\right)
		\right] \\
		&= \frac{2}{L_x L_y} \sum_\mathbf{k} \tilde{E}_\mathbf{k}
		f( \tilde{E}_\mathbf{k}; \beta,0 ) - \frac{1}{L_x L_y} \sum_\mathbf{k} \tilde{E}_\mathbf{k}
	\end{aligned}
	\]
	having used the simple property of the Fermi-Dirac distribution $f(-x;\beta,0) = 1-f(-x;\beta,0)$.
	\item The term originated by the identity produced by fermionic anticommutation rules in Eq.~\eqref{eq:pre-mft-ehm-cooper-filtered},
	\[
		\frac{1}{L_x L_y} \sum_\mathbf{k} \tilde{\xi}_\mathbf{k}
	\]
	averaged on the lattice.
	\item The ``leftovers'' of Eq.~\eqref{eq:sc-free-energy-leftovers}, divided by $L_x L_y$.
	\item The entropic free energy
	\[
		-Ts
	\]
	with $T = 1/k_B \beta$ and $s$ the free Fermi gas entropy density for the Bogoliubov quasiparticles,
	\[
		s = -\frac{2 k_B}{L_x L_y} \sum_\mathbf{k} \left[
			\left(
				1- f( \tilde{E}_\mathbf{k}; \beta,0)
			\right) \ln \left(
			1- f( \tilde{E}_\mathbf{k}; \beta,0)
			\right) + f( \tilde{E}_\mathbf{k}; \beta,0)
			\ln f( \tilde{E}_\mathbf{k}; \beta,0)
		\right]
	\]
	We use the identity:
	\[
		\ln \left(1-\frac{1}{e^x+1}\right) = x+\ln \left(\frac{1}{e^x+1}\right)
	\]
	and reduce the above expression to:
	\begin{multline*}
		s = -\frac{2 k_B}{L_x L_y} \sum_\mathbf{k} \Big[ \ln \left(
			1- f( \tilde{E}_\mathbf{k}; \beta,0) \right) + f( \tilde{E}_\mathbf{k}; \beta,0) \ln f( \tilde{E}_\mathbf{k}; \beta,0) \\
			- \beta \tilde{E}_\mathbf{k} f( \tilde{E}_\mathbf{k}; \beta,0) - f( \tilde{E}_\mathbf{k}; \beta,0) \ln f( \tilde{E}_\mathbf{k}; \beta,0)
		\Big]
	\end{multline*}
	Second and fourth terms cancel out, while the third compensates the first one of contribution 1.
\end{enumerate}
All together, the MFT averaged free energy looks like this:
\begin{multline}\label{eq:sc-free-energy}
	f_\mathrm{MFT} [\Delta_\mathbf{k}, g_\mathbf{k}] = \frac{1}{L_x L_y} \sum_\mathbf{k} \left[
		\tilde{\xi}_\mathbf{k} - \tilde{E}_\mathbf{k} + \frac{\abs{\Delta_\mathbf{k}}^2}{2\tilde{E}_\mathbf{k}} \tanh(\frac{\beta \tilde{E}_\mathbf{k}}{2})
	\right] \\
	- 2V \sum_{\gamma\in\lbrace s^*,d \rbrace} \big| g^{(\gamma)} \big|^2 + \frac{2}{\beta L_x L_y} \sum_\mathbf{k} \ln \left(
	1- f( \tilde{E}_\mathbf{k}; \beta,0) \right)
\end{multline}
The two main differences with the commonly known expressions for $f_\mathrm{MFT}$ \cite{hutchinson2021mixed, senarath2025mixed} are the presence of bands renormalization 
	{\color{tabred}, the absence of $-\mu n$ [Why?],} 
and the $\mathcal{O}\left(g^2\right)$ correction. The latter, not only is negative for attractive $V$, a feature that can lead to superconducting phase energy lowering and stabilisation, but also it depends explicitly on the spectral amplitude of the $s^*$ and $d$-wave components of $g_\mathbf{k}$. Since as seen the $d$-wave part of $g_\mathbf{k}$ arises for mixed symmetries, this details seems to indicate an energetic preference for multi-symmetry phases.

\section{Numerical simulations}\label{sec:sc-numerical}

\todo

\subsection{HF iterative algorithm sketch}\label{subsec:sc-hf-sketch}

\todo
